---
format: 
    revealjs: 
        theme: [default, ../../css/core.scss, ../../css/colors.scss]
        height: 900
        width: 1600
highlight-style: github
execute: 
  eval: false
  echo: false
---

```{r}
#| label: define reactable theme
#| eval: true
s2_theme = reactable::reactableTheme(
    headerStyle = list(
        color = "white",
        background = "var(--s2)"
    )
) 
```

```{r}
#| label: define functions for creating interview__key
#| eval: true

#' Add leading zero to 2-digit number
#' 
#' @param x Numeric. Two-digit number to give padding
#' 
#' @importFrom stringr str_pad
pad_num <- function(x) {
    stringr::str_pad(
        string = x,
        width = 2,
        pad = 0
    )
}

#' Create valid, fake `interview__key`
#' 
#' @return Character. Valid, fake `interview__id` of form XX-XX-XX-XX
#' @importFrom glue glue
create_key <- function() {

    # draw 4 random integers between 0 and 99
    nums <- sample(
        x = 0:99,
        size = 4,
        replace = TRUE
    )
    
    # construct key like XX-XX-XX-XX, where XX is a number with leading zero
    key <- glue::glue("{pad_num(nums[1])}-{pad_num(nums[2])}-{pad_num(nums[3])}-{pad_num(nums[4])}")

    return(key)

}

#' Create N valid, fake `interview__key` values
#' 
#' @param n Numeric. Number of `interview__key` values to return
#' 
#' @return Character vector. Composed of valid `interview__key` values.
#' 
#' @importFrom purrr map_chr
create_keys <- function(n) {

    purrr::map_chr(
        .x = seq(1, n),
        .f = ~ create_key()
    )

}
 
```

# Get and use Survey Solutions' data `r fontawesome::fa(name = "download")` `r fontawesome::fa(name = "magnifying-glass-chart")` {background-color=var(--suso)}

## Roadmap {.suso}

::: {.box .box-1}
Get
:::

::: {.box .box-2}
Understand
:::

::: {.box .box-3}
Use
:::

<!-- Get data -->

# Get data {background-color=var(--s1)}

## Process {.t1}

:::: {.columns}

::: {.column width="70%"}

TODO: video similar to [this one](/review_zim_course/slides_not_on_zim_site/19_get_use_data.html#/process)

:::

::: {.column width="30%"}

Select:

- Questionnaire
- Data type
- Questionnaire information*
- Data format*
- Export file destination

* Relevant only for microdata

:::

::::

## Questionnaire {.t1}

:::: {.columns}

::: {.column width="70%"}

TODO: image of UI for `Filter interviews to export`

:::

::: {.column width="30%"}

- **Questionnaire.** Title of questionnaire.
- **Questionnaire version.** Version of questionnaire. If there are multiple versions, may need to export data for each version.
- **Status.** Survey Solutions interview status. Default: all statuses.

:::

::::

## Data types {.t1}

:::: {.columns}

::: {.column width="70%"}

TODO: potentially reuse screenshot [here](/slides_not_on_zim_site/19_get_use_data.html#/types)

:::

::: {.column width="30%"}

- **Main survey data.** Otherwise known as microdata. Answers to survey questions.
- **Paradata.** Event data of all interactions / transactions with an interview.
:::

::::

## Questionnaire information {.t1}

:::: {.columns}

::: {.column width="70%"}

TODO: image of `Questionnaire information` block of export UI

:::

::: {.column width="30%"}

- **What.** Metadata that describes the questionnaire used to capture survey data and the data sets that it exports. See more [here](TODO: LINK HERE)
- **Why.** Several potential uses:
    - Document data after data collection.
    - Use metadata to assist with analyses.

:::

::::

## Data formats {.t1}

:::: {.columns}

::: {.column width="70%"}

TODO: potentially reuse screenshot [here](/review_zim_course/slides_not_on_zim_site/19_get_use_data.html#/formats) 

:::

::: {.column width="30%"}

- **Tab-delimited.** Data in flat files. Labels provided in Stata `.do` files.
- **Stata.** Compiled `.dta` files, with variable and value labels applied.
- **SPSS.** Compiled `.sav`, with variable and value labels applied.

:::

::::

## Export file destination {.t1}

:::: {.columns}

::: {.column width="70%"}

TODO: image of `Export file destination` interface on `Data Export` 

:::

::: {.column width="30%"}

- **Download.** To the device fetching the export archive. Default option.
- **Upload.** To a cloud service provider using your credentials. 
    - First, click the cloud option.
    - Then, select your profile / provide your credentials.

:::

::::

# Understand data {background-color=var(--s2)}

## Data types {.t2}

:::: {.columns}

::: {.column width="50%"}

### Two types of data

::: {.box .box-2}
Main survey data
:::

::: {.box .box-2}
Paradata
:::

:::

::: {.column width="50%" .fragment}

### But only discuss one today

::: {.box .box-2}
Main survey data
:::

:::

::::

## Roadmap `r fontawesome::fa(name = "route")` {.t2}

::: {.box .box-2}
File overview `r fontawesome::fa(name = "folder-tree")`
:::

::: {.box .box-2}
Files `r fontawesome::fa(name = "arrow-right-arrow-left")` questionnaire
:::

::: {.box .box-2}
Variables `r fontawesome::fa(name = "arrow-right-arrow-left")` questionnaire
:::

::: {.box .box-2}
Identifiers `r fontawesome::fa(name = "id-card")`
:::

::: {.box .box-2}
Missing values `r fontawesome::fa(name = "notdef")`
:::

# File overview `r fontawesome::fa(name = "folder-tree")` {background-color=var(--s1)}

## Exported data {.t2}

:::: {.columns}

::: {.column width="50%"}

### Get a zip archive

<br><br>

`r fontawesome::fa(name = "file-zipper", height = "400px")`

:::

::: {.column width="50%" .fragment}

### Files found inside

```
TODO: files exported for "Capturing What Matters"

├── assignment__actions.dta
├── Commodities_non_food_1mon.dta
├── export__readme.txt
├── facility_distance_roster.dta
├── FAFH_roster.dta
├── hhmembers.dta
├── hh_assets_roster.dta
├── International_Migration.dta
├── interview__actions.dta
├── interview__comments.dta
├── interview__diagnostics.dta
├── interview__errors.dta
├── livestock.dta
├── Questionnaire
│   ├── Categories
│   ├── content.zip
│   ├── ddi.xml
│   ├── document.json
│   └── Preview
├── social_safety_nets.dta
└── ZiHBS_2023_Actual_pilot.dta
```

:::

::::

## Export file manifest {.t2}

:::: {.columns}

::: {.column width="30%"}

```{.text code-line-numbers="5"}
TODO: files exported for "Capturing What Matters"

├── assignment__actions.dta
├── Commodities_non_food_1mon.dta
├── export__readme.txt
├── facility_distance_roster.dta
├── FAFH_roster.dta
├── hhmembers.dta
├── hh_assets_roster.dta
├── International_Migration.dta
├── interview__actions.dta
├── interview__comments.dta
├── interview__diagnostics.dta
├── interview__errors.dta
├── livestock.dta
├── Questionnaire
│   ├── Categories
│   ├── content.zip
│   ├── ddi.xml
│   ├── document.json
│   └── Preview
├── social_safety_nets.dta
└── ZiHBS_2023_Actual_pilot.dta
```

:::

::: {.column width="70%"}

```{.text}
- TODO: add code block containing text from `export__readme.txt` from "Capturing What Matters"
- TODO: use `code-line-numbers` to walk through code and explain

Generated by Survey Solutions export module 23.06.1 (build 34560) on Saturday, 16 September 2023
The data in this download were collected using the Survey Solutions questionnaire "ZiHBS 2023 Actual Pilot". 
You can open the questionnaire in the Survey Solutions Designer online by that link: https://designer.mysurvey.solutions/questionnaire/details/07a29ec50a0f4b5f9a7f45dd591d2514$2

ZiHBS_2023_Actual_pilot.dta
cp_province, cp_district, cp_ward, cp_sector, cp_ea, cp_region, cp_geocode, cp_area, cp_structure, cp_hhnumber, cp_hhid, cp_hhead, cp_phoneno, cp_address, cp_gps, cp_main, st_supname, st_intname, st_identified, st_HHmove, M1_Q0a, M1_Q0b, M1_start_date, M1_Q01, M1_Q02, M1_Q03, M1_Q04, M1_Q05, M2_START_DATE, M2_Q01, M3_start_date_time, M3_respondent, M3_Q00, M3_Q01, M4_start_date, M4_respondent, M4_Q01, M4_Q01_oth, M4_Q01a, M4_Q01b_Amt, M5_Q01b_Curr, M4_Q01c_Amt, M4_Q01c_Curr, M4_Q02, M4_Q02_oth, M4_Q03, M4_Q03_oth, M4_Q04, M4_Q04_oth, M4_Q05, M4_Q05_oth, M4_Q06, M4_Q07, M4_Q08, M4_Q08_oth, M4_Q09, M4_Q09_oth, M4_Q10, M4_Q10_oth, M4_Q11, M4_Q12, M4_Q13, M4_Q13_oth, M4_Q14, M4_Q14_oth, M4_Q15, M4_Q15_oth, M4_Q16, M4_Q16_oth, M4_Q17, M4_Q18, M4_Q18_oth, M4_Q19, M4_Q19_oth, M4_Q20, M4_Q21, M4_Q22, M4_Q23, M4_Q24, M4_Q24_oth, M4_Q25, M4_Q25_oth, M4_Q26, H27, M4_Q28, M4_Q28_oth, M4_Q29, M4_Q30, M4_Q31, M4_Q32, M4_Q33, M4_Q33_oth, M4_Q34, M4_Q35, M4_Q35_oth, M4_Q37, M4_Q38a_Amt, M4_Q38a_Curr, M4_Q38b_Amt, M4_Q38b_Curr, M4_Q38c_Amt, M4_Q38c_Curr, M5_15d_Amt, M4_Q38d_Curr, M4_Q39, M4_Q40_Amt, M5_Q40b_Curr, M8_start_date_time, M8_respondent, M8_Q01, M9_START_DATE, M10_START_DATE, M10_RESPONDENT, M11_start_date, M11_respondent, M12_start_date, M13_start_date, M14_start_date_time, M14_Q00, M14_Q01, M14_Q0E1, M15_Q02a, M16_StartTime, M16_respondent, M16_Q1a, M16_Q1b, M16_Q1c, M16_Q1d, M16_Q1B2, M16_Q2a, M16_Q2b, M16_Q2c, M16_Q2d, M16_Q2B2, M16_Q3a, M16_Q3b, M16_Q3c, M16_Q3d, M16_Q3B2, M16_Q4a, M16_Q4b, Module17_start_date, Respondent_for_module17, M17_01B, M17_Q01, M18_startDateTime, M18_respondent, M18_Q01, Q18_Q02, M18_Q11_amt, M18_Q11_cuur, M18_Q12, M18_Q13_amt, M18_Q13_cuur, M19_START_DATE, M19_RESPONDENT, M19_Q01, M20_START_DATE, M20_RESPONDENT, M21_Starting_Time, M21_Q01, M21_FAFH, M22A_StartTime, M22A_respondent, M22A_Q02_EXPENDITURE, check_M22A_complete, M22A_Q02_cereals, M22A_Q02_flours, M22A_Q02_bakery, M22A_Q02_BF_cereals, M22A_Q02_pasta, M22A_Q02_OthCreals, M22A_Q02_LiveAnimal, M22A_Q02_Meat_fresh, M22A_Q02_Meat_dried, M22A_Q02_Offal_blood, M22A_Q02_meat_prep, M22A_Q02_Fish_fresh, M22A_Q02_Fish_dried, M22A_Q02_Fish_prep, M22A_Q02_OthSFFresh, M22A_Q02_OtSFDried, M22A_Q02_oth_sf_prep, M22A_Q02_milk_raw, M22A_Q02_MilkSkimm, M22A_Q02_OthMilkCre, M22A_Q02_NonAni_milk, M22A_Q02_Cheese, M22A_Q02_Yoghurt, M22A_Q02_MilkDessert, M22A_Q02_Eggs, M22A_Q02_Vege_oils, M22A_Q02_Butter_fats, M22A_Q02_Margarine, M22A_Q02_Oth_Ani_fat, M22A_Q02_Tropi_fruit, M22A_Q02_CitrusFrt, M22A_Q02_StoneFrut, M22A_Q02_BerriyFresh, M22A_Q02_Oth_fruit_f, M22A_Q02_FrozFruit, M22A_Q02_Fruit_dried, M22A_Q02_Nuts, M22A_Q02_Fr_nut_prep, M22A_Q02_Leafy_veg, M22A_Q02_Fruit_veg, M22A_Q02_Green_leg, M22A_Q02_Ot_veg_tube, M22A_Q02_potatoes, M22A_Q02_Pulses, M22A_Q02_OtVegiDried, M22A_Q02_vegi_froze, M22A_Q02_Vegi_prep, M22A_Q02_Cane_sugar, M22A_Q02_Other_sugar, M22A_Q02_Jams, M22A_Q02_Nut_paste, M22A_Q02_Chocolate, M22A_Q02_Ice_cream, M22A_Q02_gums_candy, M22A_Q02_PrepFood, M22A_Q02_Baby_food, M22A_Q02_Salt_cond, M22A_Q02_Spices, M22A_Q02_juices, M22A_Q02_Coffee, M22A_Q02_tea, M22A_Q02_CocoaDrink, M22A_Q02_Water, M22A_Q02_Soft_drinks, M22A_Q02_OthNonAlcoh, M22B_StartTime, M22B_respondent, M22B_Q01_EXPENDITURE, check_M22B_complete, M22B_Q01_cereals, M22B_Q01_flours, M22B_Q01_bakery, M22B_Q01_BF_cereals, M22B_Q01_pasta, M22B_Q01_OthCreals, M22B_Q01_LiveAnimal, M22B_Q01_Meat_fresh, M22B_Q01_Meat_dried, M22B_Q01_Offal_blood, M22B_Q01_meat_prep, M22B_Q01_Fish_fresh, M22B_Q01_Fish_dried, M22B_Q01_Fish_prep, M22B_Q01_OthSFFresh, M22B_Q01_OtSFDried, M22B_Q01_oth_sf_prep, M22B_Q01_milk_raw, M22B_Q01_MilkSkimm, M22B_Q01_OthMilkCre, M22B_Q01_NonAni_milk, M22B_Q01_Cheese, M22B_Q01_Yoghurt, M22B_Q01_MilkDessert, M22B_Q01_Eggs, M22B_Q01_Vege_oils, M22B_Q01_Butter_fats, M22B_Q01_Margarine, M22B_Q01_Oth_Ani_fat, M22B_Q01_Tropi_fruit, M22B_Q01_CitrusFrt, M22B_Q01_StoneFrut, M22B_Q01_BerriyFresh, M22B_Q01_Oth_fruit_f, M22B_Q01_FrozFruit, M22B_Q01_Fruit_dried, M22B_Q01_Nuts, M22B_Q01_Fr_nut_prep, M22B_Q01_Leafy_veg, M22B_Q01_Fruit_veg, M22B_Q01_Green_leg, M22B_Q01_Ot_veg_tube, M22B_Q01_potatoes, M22B_Q01_Pulses, M22B_Q01_OtVegiDried, M22B_Q01_vegi_froze, M22B_Q01_Vegi_prep, M22B_Q01_Cane_sugar, M22B_Q01_Other_sugar, M22B_Q01_Jams, M22B_Q01_Nut_paste, M22B_Q01_Chocolate, M22B_Q01_Ice_cream, M22B_Q01_gums_candy, M22B_Q01_PrepFood, M22B_Q01_Baby_food, M22B_Q01_Salt_cond, M22B_Q01_Spices, M22B_Q01_juices, M22B_Q01_Coffee, M22B_Q01_tea, M22B_Q01_CocoaDrink, M22B_Q01_Water, M22B_Q01_Soft_drinks, M22B_Q01_OthNonAlcoh, M23A_start_date, M23A_respondent, M23A_Q01, M23A_Q02_check, M23A_Q02_SpiritsLiq, M23A_Q02_WineGrapes, M23A_Q02_CiderPerry, M23A_Q02_Beer, M23A_Q02_Cigarettes, M23A_Q02_Cigars, M23A_Q02_OthTobacco, M23A_Q02_Narcotics, M23B_start_date, M23b_respondent, M23B_Q01, M23B_Q02_check, M23B_Q02_SpiritsLiq, M23B_Q02_WineGrapes, M23B_Q02_CiderPerry, M23B_Q02_Beer, M23B_Q02_Cigarettes, M23B_Q02_Cigars, M23B_Q02_OthTobacco, M23B_Q02_Narcotics, Module24_start_date, Respondent_for_module_24, M24_Q01, M25_start_date, M25_Respondent, M25_Q01, M25b_start_date, M25b_Respondent, M25b_Q01, M26_start_date, M26_Respondent, M26_Q01, M27_start_date, M27_Respondent, M27_Q01, M28a_start_date, M28a_Respondent, M28a_Q01, M28b_start_date, M28b_Respondent, M28b_Q01, M29_start_date, M29_Respondent, M29_Q01, M30_start_date, M30_Respondent, M30_Q01, M31_start_date, M31_Respondent, M31_Q01, M32_START_DATE, M32_RESPONDENT, M32_Q00, M33_Start_Date, M33_respondent, M33_Q1, M33_Q2, M33_Q3, M33_Q4, M33_Q5, M33_Q6, M34_StartTime, M34_respondent, M34_Q1a, M34_Q1b, M34_Q1c, M34_Q1d, M34_Q1e, M34_Q1f, M34_Q1g, M34_Q1h, M35_StartTime, M35_respondent, M35_Q01, M35_Q02, M35_Q03, M35_Q04, M35_Q05, M35_Q06, M35_Q07, M35_Q08, M35_Q09, M35_Q10, M35_Q11, M35_Q12, M35_Q13, M35_Q14, M35_Q15, M36_Q01a, M36_Q02a1, M36_Q02_1, M36_Q01b, M36_Q02a2, M36_Q02_2, M36_Q01c, M36_Q02a3, M36_Q02_3, M36_Q03, M36_Q04a, M36_Q04b, M36_Q04c, M36_Q04c_oth

hhmembers.dta
M2_Q02, M2_Q03, M2_Q04, M2_Q05, M2_Q06, M2_Q07, M2_Q08, M2_Q09, M2_Q10, M2_Q11, M2_Q12, M2_Q13, M2_Q14, M2_Q14_OTH, M2_Q15, M2_Q16, M2_Q17, M2_Q18, M2_Q19, M2_Q20, M2_Q21, M2_Q21_ISCO, M2_Q22, M2_Q23, M2_Q24, M2_Q25, M2_Q26, M2_Q26_ISIC, M2_Q27, M2_Q28, M2_Q29_auth, M2_Q29, M9_Q0respondent, M9_RES_ID, M9_Q01, M9_Q02, M2_Q02_oth, M9_Q03, M9_Q03a, M9_Q04, M9_Q05, M9_Q06, M2_Q06_oth, M9_Q07, M9_Q07_oth, M9_Q08, M9_Q09, M9_Q10, M9_Q11, M9_Q11_oth, M9_Q12, M9_Q13_amt, M9_Q13_curr, M9_Q14, M9_Q15, M9_Q16_AMT, M9_Q16_curr, M9_Q17, M9_Q18_AMT, M9_Q18_Curr, M9_Q19, M9_Q20, M9_Q21_AMT, M9_Q21_Curr, M9_Q22, M9_Q22_oth, M9_Q23, M9_Q24, M10_Q0respondent, M10_RES_ID, M10_Q01, M10_Q02, M10_Q03, M10_Q04, M10_Q06, M10_Q07, M10_Q08, M10_Q09, M10_Q10, M10_Q11, M10_Q12, M10_Q13, M10_Q14, M10_Q14_oth, M10_Q15, M10_Q15_oth, M10_Q16, M10_Q17, M10_Q17ISCO, M10_Q18, M10_Q18_ISIC, M10_Q19, M10_Q20, M10_Q21, M10_Q22, M10_Q23, M10_Q23_oth, M10_Q24, M10_Q25, M10_Q26, M10_Q27, M10_Q28, M10_Q28_ISCO, M10_Q29, M10_Q29_ISIC, M11_Q0respondent, M11_RES_ID, M11_Q01, M11_Q02, M11_Q02_oth, M11_Q03, M11_Q03_oth, M11_Q04, M11_Q04_oth, M11_Q05, M11_Q05_oth, M11_Q06, M11_Q07, M11_Q07_oth, M11_Q08, M11_Q09, M11_Q10, M11_Q10_oth, M11_Q11, M11_Q12, M11_Q13, M11_Q14, M11_Q15, M11_Q16, M11_Q16_oth, M12_Q0respondent, M12_RES_ID, M12_Q01, M12_Q02, M12_Q03, M12_Q04, M12_Q05, M12_Q06, M12_Q07a, M12_Q7a_oth, M12_Q07b, M12_Q07b_oth, M12_Q07c, M12_Q07c_oth, M12_Q07d, M12_Q07d_oth, M12_Q07e, M12_Q07e_oth, M12_Q07f, M12_Q07f_oth, M12_Q08, M12_Q08_oth, M12_Q09, M13_Q0respondent, M13_RES_ID, M13_Q01, M13_Q02, M13_Q03, M13_Q04_curr, M13_Q04_amt_ZWD, M13_Q04_amt_USD, M13_Q04_amt_RAND, M13_Q04_amt_PULA, M13_Q05, M13_Q06, M13_Q07_curr, M13_Q07_amt, M13_Q08_curr, M13_Q08_amt, M13_Q09_amt, M13_Q09_curr, M13_Q10, M13_Q11_amt, M13_Q11_curr, M13_Q12, M13_Q13_amt, M13_Q13_Curr, M13_Q14, M13_Q15_amt, M13_Q15_curr, M13_Q16, M13_Q17_Amt, M13_Q17_Curr, M13_Q18

International_Migration.dta
M3_Q02, M3_Q03, M3_Q04, M3_Q05, M3_Q06, M3_Q07, M3_Q08, M3_Q09, M3_Q10, M3_Q11, M3_Q12, M3_Q13A, M3_Q13B, M3_Q14, M3_Q15, M3_Q16_amt, M3_Q16_curr, M3_Q17_amt, M3_Q18_curr

hh_assets_roster.dta
M8_Q02, M8_Q03, M8_Q04, M8_Q05_amt, M8_Q05_curr, M8_Q06, M8_Q07_amt, M8_Q07_curr

nfe_roster.dta
M15_Q02_b, M15_Q03, M15_Q04, M15_Q05, M15_Q05_oth, M15_Q06, M15_Q07, M15_Q08_amt, M15_Q08_curr, M15_Q09_amt, M15_Q09_curr, M15_Q10_amt, M15_Q10_curr, M15_Q11_a_amt, M15_Q11_a_curr, M15_Q11_b_amt, M15_Q11_b_curr, M15_Q11_c_amt, M15_Q11_c_curr, M15_Q11_d_amt, M15_Q11_d_curr, M15_Q11_e_amt, M15_Q11_e_curr, M15_Q11_f_amt, M15_Q11_f_curr, M15_Q11_g_amt, M15_Q11_g_curr, M15_Q11_h_amt, M15_Q11_h_curr, M15_Q11_j_amt, M15_Q11_j_curr, M15_Q11_k_amt, M15_Q11_k_curr, M15_Q11_l_amt, M15_Q11_l_curr, M15_Q11_m_amt, M15_Q11_m_curr, M15_Q11_n_amt, M15_Q11_n_curr, M15_Q11_o_amt, M15_Q11_o_curr, M15_Q11_o, M15_Q11_p_amt, M15_Q11_p_curr

Mod17_Crops.dta
M17_Q02b, M17_Q02, M17_Q02_UNIT, M17_Q03, M17_Q04, M17_Q05, M17_Q05_oth, M17_Q06_QTY, M17_Q06_UNIT, M17_Q07, M17_Q07_CURRENCY, M17_Q08, M17_Q09, M17_Q09_CURRENCY, M17_Q10, M17_Q10_CURRENCY, M17_Q11, M17_Q11_oth, M17_Q12, M17_Q13, M17_Q14, M17_Q15, M17_Q15_CURRENCY, M17_Q16, M17_Q17, M17_Q17_CURRENCY, M17_Q18, M17_Q19, M17_Q19_CURRENCY, M17_Q20, M17_Q21, M17_Q21_CURRENCY, M17_Q22, M17_Q23, M17_Q24, M17_Q24_CURRENCY, M17_Q25

livestock.dta
M18_Q02_oth, M18_Q03, Q18_Q04, M18_Q05_amt, M18_Q05_cuur, M18_Q06, M18_Q07, M18_Q08_amt, M18_Q08_curr, M18_Q09, M18_Q10

M19_LABOUR_INCOME_Roster.dta
M19_Q02_curr, M19_Q02_amt_ZWD, M19_Q02_amt_USD, M19_Q02_amt_RAND, M19_Q02_amt_PULA

FAFH_roster.dta
M21_Q02_amt, M21_Q02_curr, M21_Q03

M24_Q07_gifts.dta
M24_Q02_ItemList

M25_Product.dta
M25_Q02_ItemList

M25b_Product.dta
M25b_Q02_ItemList

M26_Product.dta
M26_Q02_ItemList

M27_Product.dta
M27_Q02_ItemList

M28a_Product.dta
M28a_Q02_ItemList

M28b_Product.dta
M28b_Q02_ItemList

M29_Product.dta
M29_Q02_ItemList

M30_Product.dta
M30_Q02_ItemList

M31_Product.dta
M31_Q02_ItemList

Commodities_non_food_1mon.dta
M24_Q02_Item_os, M24_Q03, M24_Q04, M24_Q05_amt, M24_Q05_curr, M24_Q06_amt, M24_Q06_curr, M24_Q07, M24_Q08a_amt_gift, M24_Q08a_curr_gift, M24_Q08b_amt_trans, M24_Q08b_curr_trans, M24_Q08c_amt_inkin, M24_Q08c_curr_inkin

M25_ITEM.dta
M25_Q02_Item_os, M25_Q03, M25_Q04, M25_Q05_amt, M25_Q05_curr, M25_Q06_amt, M25_Q06_curr, M25_Q07, M25_Q08a_amt_gift, M25_Q08a_curr_gift, M25_Q08b_amt_trans, M25_Q08b_curr_trans, M25_Q08c_amt_inkin, M25_Q08c_curr_inkin

M25b_ITEM.dta
M25b_Q02_Item_os, M25b_Q03, M25b_Q04, M25b_Q05_amt, M25b_Q05_curr, M25b_Q06_amt, M25b_Q06_curr, M25b_Q07, M25b_Q08a_amt_gift, M25b_Q08a_curr_gift, M25b_Q08b_amt_trans, M25b_Q08b_curr_trans, M25b_Q08c_amt_inkin, M25b_Q08c_curr_inkin

M26_ITEM.dta
M26_Q02_Item_os, M26_Q03, M26_Q04, M26_Q05_amt, M26_Q05_curr, M26_Q06_amt, M26_Q06_curr, M26_Q07, M26_Q08a_amt_gift, M26_Q08a_curr_gift, M26_Q08b_amt_trans, M26_Q08b_curr_trans, M26_Q08c_amt_inkin, M26_Q08c_curr_inkin

M27_ITEM.dta
M27_Q02_Item_os, M27_Q03, M27_Q04, M27_Q05_amt, M27_Q05_curr, M27_Q06_amt, M27_Q06_curr, M27_Q07, M27_Q08a_amt_gift, M27_Q08a_curr_gift, M27_Q08b_amt_trans, M27_Q08b_curr_trans, M27_Q08c_amt_inkin, M27_Q08c_curr_inkin

M28a_ITEM.dta
M28a_Q02_Item_os, M28a_Q03, M28a_Q04, M28a_Q05_amt, M28a_Q05_curr, M28a_Q06_amt, M28a_Q06_curr, M28a_Q07, M28a_Q08a_amt_gift, M28a_Q08a_curr_gift, M28a_Q08b_amt_trans, M28a_Q08b_curr_trans, M28a_Q08c_amt_inkin, M28a_Q08c_curr_inkin

M28b_ITEM.dta
M28b_Q02_Item_os, M28b_Q03, M28b_Q04, M28b_Q05_amt, M28b_Q05_curr, M28b_Q06_amt, M28b_Q06_curr, M28b_Q07, M28b_Q08a_amt_gift, M28b_Q08a_curr_gift, M28b_Q08b_amt_trans, M28b_Q08b_curr_trans, M28b_Q08c_amt_inkin, M28b_Q08c_curr_inkin

M29_ITEM.dta
M29_Q02_Item_os, M29_Q03, M29_Q04, M29_Q05_amt, M29_Q05_curr, M29_Q06_amt, M29_Q06_curr, M29_Q07, M29_Q08a_amt_gift, M29_Q08a_curr_gift, M29_Q08b_amt_trans, M29_Q08b_curr_trans, M29_Q08c_amt_inkin, M29_Q08c_curr_inkin

M30_ITEM.dta
M30_Q02_Item_os, M30_Q03, M30_Q04, M30_Q05_amt, M30_Q05_curr, M30_Q06_amt, M30_Q06_curr, M30_Q07, M30_Q08a_amt_gift, M30_Q08a_curr_gift, M30_Q08b_amt_trans, M30_Q08b_curr_trans, M30_Q08c_amt_inkin, M30_Q08c_curr_inkin

M31_ITEM.dta
M31_Q02_Item_os, M31_Q03, M31_Q04, M31_Q05_amt, M31_Q05_curr, M31_Q06_amt, M31_Q06_curr, M31_Q07, M31_Q08a_amt_gift, M31_Q08a_curr_gift, M31_Q08b_amt_trans, M31_Q08b_curr_trans, M31_Q08c_amt_inkin, M31_Q08c_curr_inkin

facility_distance_roster.dta
M4_Q36

social_safety_nets.dta
M20_Q01, M20_Q02, M20_Q03_MONTH, M20_Q03_YEAR, M20_Q04_VALUE, M20_Q04_CURRENCY, M20_Q05, M20_Q06, M20_Q07, M20_Q08, M20_Q09

M22A_Roster_A.dta
M22A_Q02_OS_A, M22A_Q03_A, M22A_Q04_A, M22A_Q05_qty_A, M22A_Q05_unit_A, M22A_Q05_size_A, M22A_Q06_amt_A, M22A_Q06_curr_A, M22A_Q07_qty_A, M22A_Q07_unit_A, M22A_Q07_size_A, M22A_Q08_amt_A, M22A_Q08_curr_A, M22A_Q09_A, M22A_Q10_qty_A, M22A_Q10_unit_A, M22A_Q10_size_A, M22A_Q11_qty_A, M22A_Q11_unit_A, M22A_Q11_size_A, M22A_Q12_qty_A, M22A_Q12_unit_A, M22A_Q12_size_A

M22A_Roster_B.dta
M22A_Q02_OS_B, M22A_Q03_B, M22A_Q04_B, M22A_Q05_qty_B, M22A_Q05_unit_B, M22A_Q05_size_B, M22A_Q06_Bmt_B, M22A_Q06_curr_B, M22A_Q07_qty_B, M22A_Q07_unit_B, M22A_Q07_size_B, M22A_Q08_Bmt_B, M22A_Q08_curr_B, M22A_Q09_B, M22A_Q10_qty_B, M22A_Q10_unit_B, M22A_Q10_size_B, M22A_Q11_qty_B, M22A_Q11_unit_B, M22A_Q11_size_B, M22A_Q12_qty_B, M22A_Q12_unit_B, M22A_Q12_size_B

M22B_Roster_A.dta
M22B_Q01_OS_A, M22B_Q03_qty_A, M22B_Q03_unit_A, M22B_Q03_size_A, M22B_Q04_A, M22B_Q05_qty_A, M22B_Q06_val_A, M22B_Q06_curr_A, M22B_Q07_qty_A, M22B_Q08_qty_A, M22B_Q09_qty_A, M22B_Q10_qty_A

M22B_Roster_B.dta
M22B_Q01_OS_B, M22B_Q03_qty_B, M22B_Q03_unit_B, M22B_Q03_size_B, M22B_Q04_B, M22B_Q05_qty_B, M22B_Q06_val_B, M22B_Q06_curr_B, M22B_Q07_qty_B, M22B_Q08_qty_B, M22B_Q09_qty_B, M22B_Q10_qty_B

M23A_Roster_A.dta
M23A_Q02_OS_A, M23A_Q03_A, M23A_Q04_A, M23A_Q05_qty_A, M23A_Q05_unit_A, M23A_Q05_size_A, M23A_Q06_amt_A, M23A_Q06_curr_A, M23A_Q07_qty_A, M23A_Q07_unit_A, M23A_Q07_size_A, M23A_Q08_amt_A, M23A_Q08_curr_A, M23A_Q09_A, M23A_Q10_qty_A, M23A_Q10_unit_A, M23A_Q10_size_A, M23A_Q11_qty_A, M23A_Q11_unit_A, M23A_Q11_size_A, M23A_Q12_qty_A, M23A_Q12_unit_A, M23A_Q12_size_A

M22B_Roster.dta
M22B_Q01_OS, M22B_Q03_qty, M22B_Q03_unit, M22B_Q03_size, M22B_Q04, M22B_Q05_qty, M22B_Q06_val, M22B_Q06_curr, M22B_Q07_qty, M22B_Q08_qty, M22B_Q09_qty, M22B_Q10_qty

Points_of_purchase.dta
M32_Q01, M32_Q01_oth

M33_domestic.dta
M33_Q7_Amt, M33_Q7_Curr, M33_Q8_Amt, M33_Q8_Curr, M33_Q9_Amt, M33_Q9_Curr, M33_Q10_Amt, M33_Q10_Curr

```

:::


::::


<!-- 
::: {.notes}

- Version of SuSo used to export
- Questionnaire version on Designer
- Data sets and variables contained in them. Interpret as follows
    - Top line: name of data set
    - Remaining line(s): variables in data set

:::
 -->

## Export file manifest {.t2}

:::: {.columns}

::: {.column width="80%"}

```{.text code-line-numbers="4"}
- TODO: add code block containing text from `export__readme.txt` from "Capturing What Matters"
- TODO: use `code-line-numbers` to walk through code and explain

Generated by Survey Solutions export module 23.06.1 (build 34560) on Saturday, 16 September 2023
The data in this download were collected using the Survey Solutions questionnaire "ZiHBS 2023 Actual Pilot". 
You can open the questionnaire in the Survey Solutions Designer online by that link: https://designer.mysurvey.solutions/questionnaire/details/07a29ec50a0f4b5f9a7f45dd591d2514$2

ZiHBS_2023_Actual_pilot.dta
cp_province, cp_district, cp_ward, cp_sector, cp_ea, cp_region, cp_geocode, cp_area, cp_structure, cp_hhnumber, cp_hhid, cp_hhead, cp_phoneno, cp_address, cp_gps, cp_main, st_supname, st_intname, st_identified, st_HHmove, M1_Q0a, M1_Q0b, M1_start_date, M1_Q01, M1_Q02, M1_Q03, M1_Q04, M1_Q05, M2_START_DATE, M2_Q01, M3_start_date_time, M3_respondent, M3_Q00, M3_Q01, M4_start_date, M4_respondent, M4_Q01, M4_Q01_oth, M4_Q01a, M4_Q01b_Amt, M5_Q01b_Curr, M4_Q01c_Amt, M4_Q01c_Curr, M4_Q02, M4_Q02_oth, M4_Q03, M4_Q03_oth, M4_Q04, M4_Q04_oth, M4_Q05, M4_Q05_oth, M4_Q06, M4_Q07, M4_Q08, M4_Q08_oth, M4_Q09, M4_Q09_oth, M4_Q10, M4_Q10_oth, M4_Q11, M4_Q12, M4_Q13, M4_Q13_oth, M4_Q14, M4_Q14_oth, M4_Q15, M4_Q15_oth, M4_Q16, M4_Q16_oth, M4_Q17, M4_Q18, M4_Q18_oth, M4_Q19, M4_Q19_oth, M4_Q20, M4_Q21, M4_Q22, M4_Q23, M4_Q24, M4_Q24_oth, M4_Q25, M4_Q25_oth, M4_Q26, H27, M4_Q28, M4_Q28_oth, M4_Q29, M4_Q30, M4_Q31, M4_Q32, M4_Q33, M4_Q33_oth, M4_Q34, M4_Q35, M4_Q35_oth, M4_Q37, M4_Q38a_Amt, M4_Q38a_Curr, M4_Q38b_Amt, M4_Q38b_Curr, M4_Q38c_Amt, M4_Q38c_Curr, M5_15d_Amt, M4_Q38d_Curr, M4_Q39, M4_Q40_Amt, M5_Q40b_Curr, M8_start_date_time, M8_respondent, M8_Q01, M9_START_DATE, M10_START_DATE, M10_RESPONDENT, M11_start_date, M11_respondent, M12_start_date, M13_start_date, M14_start_date_time, M14_Q00, M14_Q01, M14_Q0E1, M15_Q02a, M16_StartTime, M16_respondent, M16_Q1a, M16_Q1b, M16_Q1c, M16_Q1d, M16_Q1B2, M16_Q2a, M16_Q2b, M16_Q2c, M16_Q2d, M16_Q2B2, M16_Q3a, M16_Q3b, M16_Q3c, M16_Q3d, M16_Q3B2, M16_Q4a, M16_Q4b, Module17_start_date, Respondent_for_module17, M17_01B, M17_Q01, M18_startDateTime, M18_respondent, M18_Q01, Q18_Q02, M18_Q11_amt, M18_Q11_cuur, M18_Q12, M18_Q13_amt, M18_Q13_cuur, M19_START_DATE, M19_RESPONDENT, M19_Q01, M20_START_DATE, M20_RESPONDENT, M21_Starting_Time, M21_Q01, M21_FAFH, M22A_StartTime, M22A_respondent, M22A_Q02_EXPENDITURE, check_M22A_complete, M22A_Q02_cereals, M22A_Q02_flours, M22A_Q02_bakery, M22A_Q02_BF_cereals, M22A_Q02_pasta, M22A_Q02_OthCreals, M22A_Q02_LiveAnimal, M22A_Q02_Meat_fresh, M22A_Q02_Meat_dried, M22A_Q02_Offal_blood, M22A_Q02_meat_prep, M22A_Q02_Fish_fresh, M22A_Q02_Fish_dried, M22A_Q02_Fish_prep, M22A_Q02_OthSFFresh, M22A_Q02_OtSFDried, M22A_Q02_oth_sf_prep, M22A_Q02_milk_raw, M22A_Q02_MilkSkimm, M22A_Q02_OthMilkCre, M22A_Q02_NonAni_milk, M22A_Q02_Cheese, M22A_Q02_Yoghurt, M22A_Q02_MilkDessert, M22A_Q02_Eggs, M22A_Q02_Vege_oils, M22A_Q02_Butter_fats, M22A_Q02_Margarine, M22A_Q02_Oth_Ani_fat, M22A_Q02_Tropi_fruit, M22A_Q02_CitrusFrt, M22A_Q02_StoneFrut, M22A_Q02_BerriyFresh, M22A_Q02_Oth_fruit_f, M22A_Q02_FrozFruit, M22A_Q02_Fruit_dried, M22A_Q02_Nuts, M22A_Q02_Fr_nut_prep, M22A_Q02_Leafy_veg, M22A_Q02_Fruit_veg, M22A_Q02_Green_leg, M22A_Q02_Ot_veg_tube, M22A_Q02_potatoes, M22A_Q02_Pulses, M22A_Q02_OtVegiDried, M22A_Q02_vegi_froze, M22A_Q02_Vegi_prep, M22A_Q02_Cane_sugar, M22A_Q02_Other_sugar, M22A_Q02_Jams, M22A_Q02_Nut_paste, M22A_Q02_Chocolate, M22A_Q02_Ice_cream, M22A_Q02_gums_candy, M22A_Q02_PrepFood, M22A_Q02_Baby_food, M22A_Q02_Salt_cond, M22A_Q02_Spices, M22A_Q02_juices, M22A_Q02_Coffee, M22A_Q02_tea, M22A_Q02_CocoaDrink, M22A_Q02_Water, M22A_Q02_Soft_drinks, M22A_Q02_OthNonAlcoh, M22B_StartTime, M22B_respondent, M22B_Q01_EXPENDITURE, check_M22B_complete, M22B_Q01_cereals, M22B_Q01_flours, M22B_Q01_bakery, M22B_Q01_BF_cereals, M22B_Q01_pasta, M22B_Q01_OthCreals, M22B_Q01_LiveAnimal, M22B_Q01_Meat_fresh, M22B_Q01_Meat_dried, M22B_Q01_Offal_blood, M22B_Q01_meat_prep, M22B_Q01_Fish_fresh, M22B_Q01_Fish_dried, M22B_Q01_Fish_prep, M22B_Q01_OthSFFresh, M22B_Q01_OtSFDried, M22B_Q01_oth_sf_prep, M22B_Q01_milk_raw, M22B_Q01_MilkSkimm, M22B_Q01_OthMilkCre, M22B_Q01_NonAni_milk, M22B_Q01_Cheese, M22B_Q01_Yoghurt, M22B_Q01_MilkDessert, M22B_Q01_Eggs, M22B_Q01_Vege_oils, M22B_Q01_Butter_fats, M22B_Q01_Margarine, M22B_Q01_Oth_Ani_fat, M22B_Q01_Tropi_fruit, M22B_Q01_CitrusFrt, M22B_Q01_StoneFrut, M22B_Q01_BerriyFresh, M22B_Q01_Oth_fruit_f, M22B_Q01_FrozFruit, M22B_Q01_Fruit_dried, M22B_Q01_Nuts, M22B_Q01_Fr_nut_prep, M22B_Q01_Leafy_veg, M22B_Q01_Fruit_veg, M22B_Q01_Green_leg, M22B_Q01_Ot_veg_tube, M22B_Q01_potatoes, M22B_Q01_Pulses, M22B_Q01_OtVegiDried, M22B_Q01_vegi_froze, M22B_Q01_Vegi_prep, M22B_Q01_Cane_sugar, M22B_Q01_Other_sugar, M22B_Q01_Jams, M22B_Q01_Nut_paste, M22B_Q01_Chocolate, M22B_Q01_Ice_cream, M22B_Q01_gums_candy, M22B_Q01_PrepFood, M22B_Q01_Baby_food, M22B_Q01_Salt_cond, M22B_Q01_Spices, M22B_Q01_juices, M22B_Q01_Coffee, M22B_Q01_tea, M22B_Q01_CocoaDrink, M22B_Q01_Water, M22B_Q01_Soft_drinks, M22B_Q01_OthNonAlcoh, M23A_start_date, M23A_respondent, M23A_Q01, M23A_Q02_check, M23A_Q02_SpiritsLiq, M23A_Q02_WineGrapes, M23A_Q02_CiderPerry, M23A_Q02_Beer, M23A_Q02_Cigarettes, M23A_Q02_Cigars, M23A_Q02_OthTobacco, M23A_Q02_Narcotics, M23B_start_date, M23b_respondent, M23B_Q01, M23B_Q02_check, M23B_Q02_SpiritsLiq, M23B_Q02_WineGrapes, M23B_Q02_CiderPerry, M23B_Q02_Beer, M23B_Q02_Cigarettes, M23B_Q02_Cigars, M23B_Q02_OthTobacco, M23B_Q02_Narcotics, Module24_start_date, Respondent_for_module_24, M24_Q01, M25_start_date, M25_Respondent, M25_Q01, M25b_start_date, M25b_Respondent, M25b_Q01, M26_start_date, M26_Respondent, M26_Q01, M27_start_date, M27_Respondent, M27_Q01, M28a_start_date, M28a_Respondent, M28a_Q01, M28b_start_date, M28b_Respondent, M28b_Q01, M29_start_date, M29_Respondent, M29_Q01, M30_start_date, M30_Respondent, M30_Q01, M31_start_date, M31_Respondent, M31_Q01, M32_START_DATE, M32_RESPONDENT, M32_Q00, M33_Start_Date, M33_respondent, M33_Q1, M33_Q2, M33_Q3, M33_Q4, M33_Q5, M33_Q6, M34_StartTime, M34_respondent, M34_Q1a, M34_Q1b, M34_Q1c, M34_Q1d, M34_Q1e, M34_Q1f, M34_Q1g, M34_Q1h, M35_StartTime, M35_respondent, M35_Q01, M35_Q02, M35_Q03, M35_Q04, M35_Q05, M35_Q06, M35_Q07, M35_Q08, M35_Q09, M35_Q10, M35_Q11, M35_Q12, M35_Q13, M35_Q14, M35_Q15, M36_Q01a, M36_Q02a1, M36_Q02_1, M36_Q01b, M36_Q02a2, M36_Q02_2, M36_Q01c, M36_Q02a3, M36_Q02_3, M36_Q03, M36_Q04a, M36_Q04b, M36_Q04c, M36_Q04c_oth

hhmembers.dta
M2_Q02, M2_Q03, M2_Q04, M2_Q05, M2_Q06, M2_Q07, M2_Q08, M2_Q09, M2_Q10, M2_Q11, M2_Q12, M2_Q13, M2_Q14, M2_Q14_OTH, M2_Q15, M2_Q16, M2_Q17, M2_Q18, M2_Q19, M2_Q20, M2_Q21, M2_Q21_ISCO, M2_Q22, M2_Q23, M2_Q24, M2_Q25, M2_Q26, M2_Q26_ISIC, M2_Q27, M2_Q28, M2_Q29_auth, M2_Q29, M9_Q0respondent, M9_RES_ID, M9_Q01, M9_Q02, M2_Q02_oth, M9_Q03, M9_Q03a, M9_Q04, M9_Q05, M9_Q06, M2_Q06_oth, M9_Q07, M9_Q07_oth, M9_Q08, M9_Q09, M9_Q10, M9_Q11, M9_Q11_oth, M9_Q12, M9_Q13_amt, M9_Q13_curr, M9_Q14, M9_Q15, M9_Q16_AMT, M9_Q16_curr, M9_Q17, M9_Q18_AMT, M9_Q18_Curr, M9_Q19, M9_Q20, M9_Q21_AMT, M9_Q21_Curr, M9_Q22, M9_Q22_oth, M9_Q23, M9_Q24, M10_Q0respondent, M10_RES_ID, M10_Q01, M10_Q02, M10_Q03, M10_Q04, M10_Q06, M10_Q07, M10_Q08, M10_Q09, M10_Q10, M10_Q11, M10_Q12, M10_Q13, M10_Q14, M10_Q14_oth, M10_Q15, M10_Q15_oth, M10_Q16, M10_Q17, M10_Q17ISCO, M10_Q18, M10_Q18_ISIC, M10_Q19, M10_Q20, M10_Q21, M10_Q22, M10_Q23, M10_Q23_oth, M10_Q24, M10_Q25, M10_Q26, M10_Q27, M10_Q28, M10_Q28_ISCO, M10_Q29, M10_Q29_ISIC, M11_Q0respondent, M11_RES_ID, M11_Q01, M11_Q02, M11_Q02_oth, M11_Q03, M11_Q03_oth, M11_Q04, M11_Q04_oth, M11_Q05, M11_Q05_oth, M11_Q06, M11_Q07, M11_Q07_oth, M11_Q08, M11_Q09, M11_Q10, M11_Q10_oth, M11_Q11, M11_Q12, M11_Q13, M11_Q14, M11_Q15, M11_Q16, M11_Q16_oth, M12_Q0respondent, M12_RES_ID, M12_Q01, M12_Q02, M12_Q03, M12_Q04, M12_Q05, M12_Q06, M12_Q07a, M12_Q7a_oth, M12_Q07b, M12_Q07b_oth, M12_Q07c, M12_Q07c_oth, M12_Q07d, M12_Q07d_oth, M12_Q07e, M12_Q07e_oth, M12_Q07f, M12_Q07f_oth, M12_Q08, M12_Q08_oth, M12_Q09, M13_Q0respondent, M13_RES_ID, M13_Q01, M13_Q02, M13_Q03, M13_Q04_curr, M13_Q04_amt_ZWD, M13_Q04_amt_USD, M13_Q04_amt_RAND, M13_Q04_amt_PULA, M13_Q05, M13_Q06, M13_Q07_curr, M13_Q07_amt, M13_Q08_curr, M13_Q08_amt, M13_Q09_amt, M13_Q09_curr, M13_Q10, M13_Q11_amt, M13_Q11_curr, M13_Q12, M13_Q13_amt, M13_Q13_Curr, M13_Q14, M13_Q15_amt, M13_Q15_curr, M13_Q16, M13_Q17_Amt, M13_Q17_Curr, M13_Q18

International_Migration.dta
M3_Q02, M3_Q03, M3_Q04, M3_Q05, M3_Q06, M3_Q07, M3_Q08, M3_Q09, M3_Q10, M3_Q11, M3_Q12, M3_Q13A, M3_Q13B, M3_Q14, M3_Q15, M3_Q16_amt, M3_Q16_curr, M3_Q17_amt, M3_Q18_curr

hh_assets_roster.dta
M8_Q02, M8_Q03, M8_Q04, M8_Q05_amt, M8_Q05_curr, M8_Q06, M8_Q07_amt, M8_Q07_curr

nfe_roster.dta
M15_Q02_b, M15_Q03, M15_Q04, M15_Q05, M15_Q05_oth, M15_Q06, M15_Q07, M15_Q08_amt, M15_Q08_curr, M15_Q09_amt, M15_Q09_curr, M15_Q10_amt, M15_Q10_curr, M15_Q11_a_amt, M15_Q11_a_curr, M15_Q11_b_amt, M15_Q11_b_curr, M15_Q11_c_amt, M15_Q11_c_curr, M15_Q11_d_amt, M15_Q11_d_curr, M15_Q11_e_amt, M15_Q11_e_curr, M15_Q11_f_amt, M15_Q11_f_curr, M15_Q11_g_amt, M15_Q11_g_curr, M15_Q11_h_amt, M15_Q11_h_curr, M15_Q11_j_amt, M15_Q11_j_curr, M15_Q11_k_amt, M15_Q11_k_curr, M15_Q11_l_amt, M15_Q11_l_curr, M15_Q11_m_amt, M15_Q11_m_curr, M15_Q11_n_amt, M15_Q11_n_curr, M15_Q11_o_amt, M15_Q11_o_curr, M15_Q11_o, M15_Q11_p_amt, M15_Q11_p_curr

Mod17_Crops.dta
M17_Q02b, M17_Q02, M17_Q02_UNIT, M17_Q03, M17_Q04, M17_Q05, M17_Q05_oth, M17_Q06_QTY, M17_Q06_UNIT, M17_Q07, M17_Q07_CURRENCY, M17_Q08, M17_Q09, M17_Q09_CURRENCY, M17_Q10, M17_Q10_CURRENCY, M17_Q11, M17_Q11_oth, M17_Q12, M17_Q13, M17_Q14, M17_Q15, M17_Q15_CURRENCY, M17_Q16, M17_Q17, M17_Q17_CURRENCY, M17_Q18, M17_Q19, M17_Q19_CURRENCY, M17_Q20, M17_Q21, M17_Q21_CURRENCY, M17_Q22, M17_Q23, M17_Q24, M17_Q24_CURRENCY, M17_Q25

livestock.dta
M18_Q02_oth, M18_Q03, Q18_Q04, M18_Q05_amt, M18_Q05_cuur, M18_Q06, M18_Q07, M18_Q08_amt, M18_Q08_curr, M18_Q09, M18_Q10

M19_LABOUR_INCOME_Roster.dta
M19_Q02_curr, M19_Q02_amt_ZWD, M19_Q02_amt_USD, M19_Q02_amt_RAND, M19_Q02_amt_PULA

FAFH_roster.dta
M21_Q02_amt, M21_Q02_curr, M21_Q03

M24_Q07_gifts.dta
M24_Q02_ItemList

M25_Product.dta
M25_Q02_ItemList

M25b_Product.dta
M25b_Q02_ItemList

M26_Product.dta
M26_Q02_ItemList

M27_Product.dta
M27_Q02_ItemList

M28a_Product.dta
M28a_Q02_ItemList

M28b_Product.dta
M28b_Q02_ItemList

M29_Product.dta
M29_Q02_ItemList

M30_Product.dta
M30_Q02_ItemList

M31_Product.dta
M31_Q02_ItemList

Commodities_non_food_1mon.dta
M24_Q02_Item_os, M24_Q03, M24_Q04, M24_Q05_amt, M24_Q05_curr, M24_Q06_amt, M24_Q06_curr, M24_Q07, M24_Q08a_amt_gift, M24_Q08a_curr_gift, M24_Q08b_amt_trans, M24_Q08b_curr_trans, M24_Q08c_amt_inkin, M24_Q08c_curr_inkin

M25_ITEM.dta
M25_Q02_Item_os, M25_Q03, M25_Q04, M25_Q05_amt, M25_Q05_curr, M25_Q06_amt, M25_Q06_curr, M25_Q07, M25_Q08a_amt_gift, M25_Q08a_curr_gift, M25_Q08b_amt_trans, M25_Q08b_curr_trans, M25_Q08c_amt_inkin, M25_Q08c_curr_inkin

M25b_ITEM.dta
M25b_Q02_Item_os, M25b_Q03, M25b_Q04, M25b_Q05_amt, M25b_Q05_curr, M25b_Q06_amt, M25b_Q06_curr, M25b_Q07, M25b_Q08a_amt_gift, M25b_Q08a_curr_gift, M25b_Q08b_amt_trans, M25b_Q08b_curr_trans, M25b_Q08c_amt_inkin, M25b_Q08c_curr_inkin

M26_ITEM.dta
M26_Q02_Item_os, M26_Q03, M26_Q04, M26_Q05_amt, M26_Q05_curr, M26_Q06_amt, M26_Q06_curr, M26_Q07, M26_Q08a_amt_gift, M26_Q08a_curr_gift, M26_Q08b_amt_trans, M26_Q08b_curr_trans, M26_Q08c_amt_inkin, M26_Q08c_curr_inkin

M27_ITEM.dta
M27_Q02_Item_os, M27_Q03, M27_Q04, M27_Q05_amt, M27_Q05_curr, M27_Q06_amt, M27_Q06_curr, M27_Q07, M27_Q08a_amt_gift, M27_Q08a_curr_gift, M27_Q08b_amt_trans, M27_Q08b_curr_trans, M27_Q08c_amt_inkin, M27_Q08c_curr_inkin

M28a_ITEM.dta
M28a_Q02_Item_os, M28a_Q03, M28a_Q04, M28a_Q05_amt, M28a_Q05_curr, M28a_Q06_amt, M28a_Q06_curr, M28a_Q07, M28a_Q08a_amt_gift, M28a_Q08a_curr_gift, M28a_Q08b_amt_trans, M28a_Q08b_curr_trans, M28a_Q08c_amt_inkin, M28a_Q08c_curr_inkin

M28b_ITEM.dta
M28b_Q02_Item_os, M28b_Q03, M28b_Q04, M28b_Q05_amt, M28b_Q05_curr, M28b_Q06_amt, M28b_Q06_curr, M28b_Q07, M28b_Q08a_amt_gift, M28b_Q08a_curr_gift, M28b_Q08b_amt_trans, M28b_Q08b_curr_trans, M28b_Q08c_amt_inkin, M28b_Q08c_curr_inkin

M29_ITEM.dta
M29_Q02_Item_os, M29_Q03, M29_Q04, M29_Q05_amt, M29_Q05_curr, M29_Q06_amt, M29_Q06_curr, M29_Q07, M29_Q08a_amt_gift, M29_Q08a_curr_gift, M29_Q08b_amt_trans, M29_Q08b_curr_trans, M29_Q08c_amt_inkin, M29_Q08c_curr_inkin

M30_ITEM.dta
M30_Q02_Item_os, M30_Q03, M30_Q04, M30_Q05_amt, M30_Q05_curr, M30_Q06_amt, M30_Q06_curr, M30_Q07, M30_Q08a_amt_gift, M30_Q08a_curr_gift, M30_Q08b_amt_trans, M30_Q08b_curr_trans, M30_Q08c_amt_inkin, M30_Q08c_curr_inkin

M31_ITEM.dta
M31_Q02_Item_os, M31_Q03, M31_Q04, M31_Q05_amt, M31_Q05_curr, M31_Q06_amt, M31_Q06_curr, M31_Q07, M31_Q08a_amt_gift, M31_Q08a_curr_gift, M31_Q08b_amt_trans, M31_Q08b_curr_trans, M31_Q08c_amt_inkin, M31_Q08c_curr_inkin

facility_distance_roster.dta
M4_Q36

social_safety_nets.dta
M20_Q01, M20_Q02, M20_Q03_MONTH, M20_Q03_YEAR, M20_Q04_VALUE, M20_Q04_CURRENCY, M20_Q05, M20_Q06, M20_Q07, M20_Q08, M20_Q09

M22A_Roster_A.dta
M22A_Q02_OS_A, M22A_Q03_A, M22A_Q04_A, M22A_Q05_qty_A, M22A_Q05_unit_A, M22A_Q05_size_A, M22A_Q06_amt_A, M22A_Q06_curr_A, M22A_Q07_qty_A, M22A_Q07_unit_A, M22A_Q07_size_A, M22A_Q08_amt_A, M22A_Q08_curr_A, M22A_Q09_A, M22A_Q10_qty_A, M22A_Q10_unit_A, M22A_Q10_size_A, M22A_Q11_qty_A, M22A_Q11_unit_A, M22A_Q11_size_A, M22A_Q12_qty_A, M22A_Q12_unit_A, M22A_Q12_size_A

M22A_Roster_B.dta
M22A_Q02_OS_B, M22A_Q03_B, M22A_Q04_B, M22A_Q05_qty_B, M22A_Q05_unit_B, M22A_Q05_size_B, M22A_Q06_Bmt_B, M22A_Q06_curr_B, M22A_Q07_qty_B, M22A_Q07_unit_B, M22A_Q07_size_B, M22A_Q08_Bmt_B, M22A_Q08_curr_B, M22A_Q09_B, M22A_Q10_qty_B, M22A_Q10_unit_B, M22A_Q10_size_B, M22A_Q11_qty_B, M22A_Q11_unit_B, M22A_Q11_size_B, M22A_Q12_qty_B, M22A_Q12_unit_B, M22A_Q12_size_B

M22B_Roster_A.dta
M22B_Q01_OS_A, M22B_Q03_qty_A, M22B_Q03_unit_A, M22B_Q03_size_A, M22B_Q04_A, M22B_Q05_qty_A, M22B_Q06_val_A, M22B_Q06_curr_A, M22B_Q07_qty_A, M22B_Q08_qty_A, M22B_Q09_qty_A, M22B_Q10_qty_A

M22B_Roster_B.dta
M22B_Q01_OS_B, M22B_Q03_qty_B, M22B_Q03_unit_B, M22B_Q03_size_B, M22B_Q04_B, M22B_Q05_qty_B, M22B_Q06_val_B, M22B_Q06_curr_B, M22B_Q07_qty_B, M22B_Q08_qty_B, M22B_Q09_qty_B, M22B_Q10_qty_B

M23A_Roster_A.dta
M23A_Q02_OS_A, M23A_Q03_A, M23A_Q04_A, M23A_Q05_qty_A, M23A_Q05_unit_A, M23A_Q05_size_A, M23A_Q06_amt_A, M23A_Q06_curr_A, M23A_Q07_qty_A, M23A_Q07_unit_A, M23A_Q07_size_A, M23A_Q08_amt_A, M23A_Q08_curr_A, M23A_Q09_A, M23A_Q10_qty_A, M23A_Q10_unit_A, M23A_Q10_size_A, M23A_Q11_qty_A, M23A_Q11_unit_A, M23A_Q11_size_A, M23A_Q12_qty_A, M23A_Q12_unit_A, M23A_Q12_size_A

M22B_Roster.dta
M22B_Q01_OS, M22B_Q03_qty, M22B_Q03_unit, M22B_Q03_size, M22B_Q04, M22B_Q05_qty, M22B_Q06_val, M22B_Q06_curr, M22B_Q07_qty, M22B_Q08_qty, M22B_Q09_qty, M22B_Q10_qty

Points_of_purchase.dta
M32_Q01, M32_Q01_oth

M33_domestic.dta
M33_Q7_Amt, M33_Q7_Curr, M33_Q8_Amt, M33_Q8_Curr, M33_Q9_Amt, M33_Q9_Curr, M33_Q10_Amt, M33_Q10_Curr

```

:::

::: {.column width="20%"}

- Survey Solutions software version used to export
- Date of export

:::

::::

## Export file manifest {.t2}

:::: {.columns}

::: {.column width="80%"}

```{.text code-line-numbers="6"}
- TODO: add code block containing text from `export__readme.txt` from "Capturing What Matters"
- TODO: use `code-line-numbers` to walk through code and explain

Generated by Survey Solutions export module 23.06.1 (build 34560) on Saturday, 16 September 2023
The data in this download were collected using the Survey Solutions questionnaire "ZiHBS 2023 Actual Pilot". 
You can open the questionnaire in the Survey Solutions Designer online by that link: https://designer.mysurvey.solutions/questionnaire/details/07a29ec50a0f4b5f9a7f45dd591d2514$2

ZiHBS_2023_Actual_pilot.dta
cp_province, cp_district, cp_ward, cp_sector, cp_ea, cp_region, cp_geocode, cp_area, cp_structure, cp_hhnumber, cp_hhid, cp_hhead, cp_phoneno, cp_address, cp_gps, cp_main, st_supname, st_intname, st_identified, st_HHmove, M1_Q0a, M1_Q0b, M1_start_date, M1_Q01, M1_Q02, M1_Q03, M1_Q04, M1_Q05, M2_START_DATE, M2_Q01, M3_start_date_time, M3_respondent, M3_Q00, M3_Q01, M4_start_date, M4_respondent, M4_Q01, M4_Q01_oth, M4_Q01a, M4_Q01b_Amt, M5_Q01b_Curr, M4_Q01c_Amt, M4_Q01c_Curr, M4_Q02, M4_Q02_oth, M4_Q03, M4_Q03_oth, M4_Q04, M4_Q04_oth, M4_Q05, M4_Q05_oth, M4_Q06, M4_Q07, M4_Q08, M4_Q08_oth, M4_Q09, M4_Q09_oth, M4_Q10, M4_Q10_oth, M4_Q11, M4_Q12, M4_Q13, M4_Q13_oth, M4_Q14, M4_Q14_oth, M4_Q15, M4_Q15_oth, M4_Q16, M4_Q16_oth, M4_Q17, M4_Q18, M4_Q18_oth, M4_Q19, M4_Q19_oth, M4_Q20, M4_Q21, M4_Q22, M4_Q23, M4_Q24, M4_Q24_oth, M4_Q25, M4_Q25_oth, M4_Q26, H27, M4_Q28, M4_Q28_oth, M4_Q29, M4_Q30, M4_Q31, M4_Q32, M4_Q33, M4_Q33_oth, M4_Q34, M4_Q35, M4_Q35_oth, M4_Q37, M4_Q38a_Amt, M4_Q38a_Curr, M4_Q38b_Amt, M4_Q38b_Curr, M4_Q38c_Amt, M4_Q38c_Curr, M5_15d_Amt, M4_Q38d_Curr, M4_Q39, M4_Q40_Amt, M5_Q40b_Curr, M8_start_date_time, M8_respondent, M8_Q01, M9_START_DATE, M10_START_DATE, M10_RESPONDENT, M11_start_date, M11_respondent, M12_start_date, M13_start_date, M14_start_date_time, M14_Q00, M14_Q01, M14_Q0E1, M15_Q02a, M16_StartTime, M16_respondent, M16_Q1a, M16_Q1b, M16_Q1c, M16_Q1d, M16_Q1B2, M16_Q2a, M16_Q2b, M16_Q2c, M16_Q2d, M16_Q2B2, M16_Q3a, M16_Q3b, M16_Q3c, M16_Q3d, M16_Q3B2, M16_Q4a, M16_Q4b, Module17_start_date, Respondent_for_module17, M17_01B, M17_Q01, M18_startDateTime, M18_respondent, M18_Q01, Q18_Q02, M18_Q11_amt, M18_Q11_cuur, M18_Q12, M18_Q13_amt, M18_Q13_cuur, M19_START_DATE, M19_RESPONDENT, M19_Q01, M20_START_DATE, M20_RESPONDENT, M21_Starting_Time, M21_Q01, M21_FAFH, M22A_StartTime, M22A_respondent, M22A_Q02_EXPENDITURE, check_M22A_complete, M22A_Q02_cereals, M22A_Q02_flours, M22A_Q02_bakery, M22A_Q02_BF_cereals, M22A_Q02_pasta, M22A_Q02_OthCreals, M22A_Q02_LiveAnimal, M22A_Q02_Meat_fresh, M22A_Q02_Meat_dried, M22A_Q02_Offal_blood, M22A_Q02_meat_prep, M22A_Q02_Fish_fresh, M22A_Q02_Fish_dried, M22A_Q02_Fish_prep, M22A_Q02_OthSFFresh, M22A_Q02_OtSFDried, M22A_Q02_oth_sf_prep, M22A_Q02_milk_raw, M22A_Q02_MilkSkimm, M22A_Q02_OthMilkCre, M22A_Q02_NonAni_milk, M22A_Q02_Cheese, M22A_Q02_Yoghurt, M22A_Q02_MilkDessert, M22A_Q02_Eggs, M22A_Q02_Vege_oils, M22A_Q02_Butter_fats, M22A_Q02_Margarine, M22A_Q02_Oth_Ani_fat, M22A_Q02_Tropi_fruit, M22A_Q02_CitrusFrt, M22A_Q02_StoneFrut, M22A_Q02_BerriyFresh, M22A_Q02_Oth_fruit_f, M22A_Q02_FrozFruit, M22A_Q02_Fruit_dried, M22A_Q02_Nuts, M22A_Q02_Fr_nut_prep, M22A_Q02_Leafy_veg, M22A_Q02_Fruit_veg, M22A_Q02_Green_leg, M22A_Q02_Ot_veg_tube, M22A_Q02_potatoes, M22A_Q02_Pulses, M22A_Q02_OtVegiDried, M22A_Q02_vegi_froze, M22A_Q02_Vegi_prep, M22A_Q02_Cane_sugar, M22A_Q02_Other_sugar, M22A_Q02_Jams, M22A_Q02_Nut_paste, M22A_Q02_Chocolate, M22A_Q02_Ice_cream, M22A_Q02_gums_candy, M22A_Q02_PrepFood, M22A_Q02_Baby_food, M22A_Q02_Salt_cond, M22A_Q02_Spices, M22A_Q02_juices, M22A_Q02_Coffee, M22A_Q02_tea, M22A_Q02_CocoaDrink, M22A_Q02_Water, M22A_Q02_Soft_drinks, M22A_Q02_OthNonAlcoh, M22B_StartTime, M22B_respondent, M22B_Q01_EXPENDITURE, check_M22B_complete, M22B_Q01_cereals, M22B_Q01_flours, M22B_Q01_bakery, M22B_Q01_BF_cereals, M22B_Q01_pasta, M22B_Q01_OthCreals, M22B_Q01_LiveAnimal, M22B_Q01_Meat_fresh, M22B_Q01_Meat_dried, M22B_Q01_Offal_blood, M22B_Q01_meat_prep, M22B_Q01_Fish_fresh, M22B_Q01_Fish_dried, M22B_Q01_Fish_prep, M22B_Q01_OthSFFresh, M22B_Q01_OtSFDried, M22B_Q01_oth_sf_prep, M22B_Q01_milk_raw, M22B_Q01_MilkSkimm, M22B_Q01_OthMilkCre, M22B_Q01_NonAni_milk, M22B_Q01_Cheese, M22B_Q01_Yoghurt, M22B_Q01_MilkDessert, M22B_Q01_Eggs, M22B_Q01_Vege_oils, M22B_Q01_Butter_fats, M22B_Q01_Margarine, M22B_Q01_Oth_Ani_fat, M22B_Q01_Tropi_fruit, M22B_Q01_CitrusFrt, M22B_Q01_StoneFrut, M22B_Q01_BerriyFresh, M22B_Q01_Oth_fruit_f, M22B_Q01_FrozFruit, M22B_Q01_Fruit_dried, M22B_Q01_Nuts, M22B_Q01_Fr_nut_prep, M22B_Q01_Leafy_veg, M22B_Q01_Fruit_veg, M22B_Q01_Green_leg, M22B_Q01_Ot_veg_tube, M22B_Q01_potatoes, M22B_Q01_Pulses, M22B_Q01_OtVegiDried, M22B_Q01_vegi_froze, M22B_Q01_Vegi_prep, M22B_Q01_Cane_sugar, M22B_Q01_Other_sugar, M22B_Q01_Jams, M22B_Q01_Nut_paste, M22B_Q01_Chocolate, M22B_Q01_Ice_cream, M22B_Q01_gums_candy, M22B_Q01_PrepFood, M22B_Q01_Baby_food, M22B_Q01_Salt_cond, M22B_Q01_Spices, M22B_Q01_juices, M22B_Q01_Coffee, M22B_Q01_tea, M22B_Q01_CocoaDrink, M22B_Q01_Water, M22B_Q01_Soft_drinks, M22B_Q01_OthNonAlcoh, M23A_start_date, M23A_respondent, M23A_Q01, M23A_Q02_check, M23A_Q02_SpiritsLiq, M23A_Q02_WineGrapes, M23A_Q02_CiderPerry, M23A_Q02_Beer, M23A_Q02_Cigarettes, M23A_Q02_Cigars, M23A_Q02_OthTobacco, M23A_Q02_Narcotics, M23B_start_date, M23b_respondent, M23B_Q01, M23B_Q02_check, M23B_Q02_SpiritsLiq, M23B_Q02_WineGrapes, M23B_Q02_CiderPerry, M23B_Q02_Beer, M23B_Q02_Cigarettes, M23B_Q02_Cigars, M23B_Q02_OthTobacco, M23B_Q02_Narcotics, Module24_start_date, Respondent_for_module_24, M24_Q01, M25_start_date, M25_Respondent, M25_Q01, M25b_start_date, M25b_Respondent, M25b_Q01, M26_start_date, M26_Respondent, M26_Q01, M27_start_date, M27_Respondent, M27_Q01, M28a_start_date, M28a_Respondent, M28a_Q01, M28b_start_date, M28b_Respondent, M28b_Q01, M29_start_date, M29_Respondent, M29_Q01, M30_start_date, M30_Respondent, M30_Q01, M31_start_date, M31_Respondent, M31_Q01, M32_START_DATE, M32_RESPONDENT, M32_Q00, M33_Start_Date, M33_respondent, M33_Q1, M33_Q2, M33_Q3, M33_Q4, M33_Q5, M33_Q6, M34_StartTime, M34_respondent, M34_Q1a, M34_Q1b, M34_Q1c, M34_Q1d, M34_Q1e, M34_Q1f, M34_Q1g, M34_Q1h, M35_StartTime, M35_respondent, M35_Q01, M35_Q02, M35_Q03, M35_Q04, M35_Q05, M35_Q06, M35_Q07, M35_Q08, M35_Q09, M35_Q10, M35_Q11, M35_Q12, M35_Q13, M35_Q14, M35_Q15, M36_Q01a, M36_Q02a1, M36_Q02_1, M36_Q01b, M36_Q02a2, M36_Q02_2, M36_Q01c, M36_Q02a3, M36_Q02_3, M36_Q03, M36_Q04a, M36_Q04b, M36_Q04c, M36_Q04c_oth

hhmembers.dta
M2_Q02, M2_Q03, M2_Q04, M2_Q05, M2_Q06, M2_Q07, M2_Q08, M2_Q09, M2_Q10, M2_Q11, M2_Q12, M2_Q13, M2_Q14, M2_Q14_OTH, M2_Q15, M2_Q16, M2_Q17, M2_Q18, M2_Q19, M2_Q20, M2_Q21, M2_Q21_ISCO, M2_Q22, M2_Q23, M2_Q24, M2_Q25, M2_Q26, M2_Q26_ISIC, M2_Q27, M2_Q28, M2_Q29_auth, M2_Q29, M9_Q0respondent, M9_RES_ID, M9_Q01, M9_Q02, M2_Q02_oth, M9_Q03, M9_Q03a, M9_Q04, M9_Q05, M9_Q06, M2_Q06_oth, M9_Q07, M9_Q07_oth, M9_Q08, M9_Q09, M9_Q10, M9_Q11, M9_Q11_oth, M9_Q12, M9_Q13_amt, M9_Q13_curr, M9_Q14, M9_Q15, M9_Q16_AMT, M9_Q16_curr, M9_Q17, M9_Q18_AMT, M9_Q18_Curr, M9_Q19, M9_Q20, M9_Q21_AMT, M9_Q21_Curr, M9_Q22, M9_Q22_oth, M9_Q23, M9_Q24, M10_Q0respondent, M10_RES_ID, M10_Q01, M10_Q02, M10_Q03, M10_Q04, M10_Q06, M10_Q07, M10_Q08, M10_Q09, M10_Q10, M10_Q11, M10_Q12, M10_Q13, M10_Q14, M10_Q14_oth, M10_Q15, M10_Q15_oth, M10_Q16, M10_Q17, M10_Q17ISCO, M10_Q18, M10_Q18_ISIC, M10_Q19, M10_Q20, M10_Q21, M10_Q22, M10_Q23, M10_Q23_oth, M10_Q24, M10_Q25, M10_Q26, M10_Q27, M10_Q28, M10_Q28_ISCO, M10_Q29, M10_Q29_ISIC, M11_Q0respondent, M11_RES_ID, M11_Q01, M11_Q02, M11_Q02_oth, M11_Q03, M11_Q03_oth, M11_Q04, M11_Q04_oth, M11_Q05, M11_Q05_oth, M11_Q06, M11_Q07, M11_Q07_oth, M11_Q08, M11_Q09, M11_Q10, M11_Q10_oth, M11_Q11, M11_Q12, M11_Q13, M11_Q14, M11_Q15, M11_Q16, M11_Q16_oth, M12_Q0respondent, M12_RES_ID, M12_Q01, M12_Q02, M12_Q03, M12_Q04, M12_Q05, M12_Q06, M12_Q07a, M12_Q7a_oth, M12_Q07b, M12_Q07b_oth, M12_Q07c, M12_Q07c_oth, M12_Q07d, M12_Q07d_oth, M12_Q07e, M12_Q07e_oth, M12_Q07f, M12_Q07f_oth, M12_Q08, M12_Q08_oth, M12_Q09, M13_Q0respondent, M13_RES_ID, M13_Q01, M13_Q02, M13_Q03, M13_Q04_curr, M13_Q04_amt_ZWD, M13_Q04_amt_USD, M13_Q04_amt_RAND, M13_Q04_amt_PULA, M13_Q05, M13_Q06, M13_Q07_curr, M13_Q07_amt, M13_Q08_curr, M13_Q08_amt, M13_Q09_amt, M13_Q09_curr, M13_Q10, M13_Q11_amt, M13_Q11_curr, M13_Q12, M13_Q13_amt, M13_Q13_Curr, M13_Q14, M13_Q15_amt, M13_Q15_curr, M13_Q16, M13_Q17_Amt, M13_Q17_Curr, M13_Q18

International_Migration.dta
M3_Q02, M3_Q03, M3_Q04, M3_Q05, M3_Q06, M3_Q07, M3_Q08, M3_Q09, M3_Q10, M3_Q11, M3_Q12, M3_Q13A, M3_Q13B, M3_Q14, M3_Q15, M3_Q16_amt, M3_Q16_curr, M3_Q17_amt, M3_Q18_curr

hh_assets_roster.dta
M8_Q02, M8_Q03, M8_Q04, M8_Q05_amt, M8_Q05_curr, M8_Q06, M8_Q07_amt, M8_Q07_curr

nfe_roster.dta
M15_Q02_b, M15_Q03, M15_Q04, M15_Q05, M15_Q05_oth, M15_Q06, M15_Q07, M15_Q08_amt, M15_Q08_curr, M15_Q09_amt, M15_Q09_curr, M15_Q10_amt, M15_Q10_curr, M15_Q11_a_amt, M15_Q11_a_curr, M15_Q11_b_amt, M15_Q11_b_curr, M15_Q11_c_amt, M15_Q11_c_curr, M15_Q11_d_amt, M15_Q11_d_curr, M15_Q11_e_amt, M15_Q11_e_curr, M15_Q11_f_amt, M15_Q11_f_curr, M15_Q11_g_amt, M15_Q11_g_curr, M15_Q11_h_amt, M15_Q11_h_curr, M15_Q11_j_amt, M15_Q11_j_curr, M15_Q11_k_amt, M15_Q11_k_curr, M15_Q11_l_amt, M15_Q11_l_curr, M15_Q11_m_amt, M15_Q11_m_curr, M15_Q11_n_amt, M15_Q11_n_curr, M15_Q11_o_amt, M15_Q11_o_curr, M15_Q11_o, M15_Q11_p_amt, M15_Q11_p_curr

Mod17_Crops.dta
M17_Q02b, M17_Q02, M17_Q02_UNIT, M17_Q03, M17_Q04, M17_Q05, M17_Q05_oth, M17_Q06_QTY, M17_Q06_UNIT, M17_Q07, M17_Q07_CURRENCY, M17_Q08, M17_Q09, M17_Q09_CURRENCY, M17_Q10, M17_Q10_CURRENCY, M17_Q11, M17_Q11_oth, M17_Q12, M17_Q13, M17_Q14, M17_Q15, M17_Q15_CURRENCY, M17_Q16, M17_Q17, M17_Q17_CURRENCY, M17_Q18, M17_Q19, M17_Q19_CURRENCY, M17_Q20, M17_Q21, M17_Q21_CURRENCY, M17_Q22, M17_Q23, M17_Q24, M17_Q24_CURRENCY, M17_Q25

livestock.dta
M18_Q02_oth, M18_Q03, Q18_Q04, M18_Q05_amt, M18_Q05_cuur, M18_Q06, M18_Q07, M18_Q08_amt, M18_Q08_curr, M18_Q09, M18_Q10

M19_LABOUR_INCOME_Roster.dta
M19_Q02_curr, M19_Q02_amt_ZWD, M19_Q02_amt_USD, M19_Q02_amt_RAND, M19_Q02_amt_PULA

FAFH_roster.dta
M21_Q02_amt, M21_Q02_curr, M21_Q03

M24_Q07_gifts.dta
M24_Q02_ItemList

M25_Product.dta
M25_Q02_ItemList

M25b_Product.dta
M25b_Q02_ItemList

M26_Product.dta
M26_Q02_ItemList

M27_Product.dta
M27_Q02_ItemList

M28a_Product.dta
M28a_Q02_ItemList

M28b_Product.dta
M28b_Q02_ItemList

M29_Product.dta
M29_Q02_ItemList

M30_Product.dta
M30_Q02_ItemList

M31_Product.dta
M31_Q02_ItemList

Commodities_non_food_1mon.dta
M24_Q02_Item_os, M24_Q03, M24_Q04, M24_Q05_amt, M24_Q05_curr, M24_Q06_amt, M24_Q06_curr, M24_Q07, M24_Q08a_amt_gift, M24_Q08a_curr_gift, M24_Q08b_amt_trans, M24_Q08b_curr_trans, M24_Q08c_amt_inkin, M24_Q08c_curr_inkin

M25_ITEM.dta
M25_Q02_Item_os, M25_Q03, M25_Q04, M25_Q05_amt, M25_Q05_curr, M25_Q06_amt, M25_Q06_curr, M25_Q07, M25_Q08a_amt_gift, M25_Q08a_curr_gift, M25_Q08b_amt_trans, M25_Q08b_curr_trans, M25_Q08c_amt_inkin, M25_Q08c_curr_inkin

M25b_ITEM.dta
M25b_Q02_Item_os, M25b_Q03, M25b_Q04, M25b_Q05_amt, M25b_Q05_curr, M25b_Q06_amt, M25b_Q06_curr, M25b_Q07, M25b_Q08a_amt_gift, M25b_Q08a_curr_gift, M25b_Q08b_amt_trans, M25b_Q08b_curr_trans, M25b_Q08c_amt_inkin, M25b_Q08c_curr_inkin

M26_ITEM.dta
M26_Q02_Item_os, M26_Q03, M26_Q04, M26_Q05_amt, M26_Q05_curr, M26_Q06_amt, M26_Q06_curr, M26_Q07, M26_Q08a_amt_gift, M26_Q08a_curr_gift, M26_Q08b_amt_trans, M26_Q08b_curr_trans, M26_Q08c_amt_inkin, M26_Q08c_curr_inkin

M27_ITEM.dta
M27_Q02_Item_os, M27_Q03, M27_Q04, M27_Q05_amt, M27_Q05_curr, M27_Q06_amt, M27_Q06_curr, M27_Q07, M27_Q08a_amt_gift, M27_Q08a_curr_gift, M27_Q08b_amt_trans, M27_Q08b_curr_trans, M27_Q08c_amt_inkin, M27_Q08c_curr_inkin

M28a_ITEM.dta
M28a_Q02_Item_os, M28a_Q03, M28a_Q04, M28a_Q05_amt, M28a_Q05_curr, M28a_Q06_amt, M28a_Q06_curr, M28a_Q07, M28a_Q08a_amt_gift, M28a_Q08a_curr_gift, M28a_Q08b_amt_trans, M28a_Q08b_curr_trans, M28a_Q08c_amt_inkin, M28a_Q08c_curr_inkin

M28b_ITEM.dta
M28b_Q02_Item_os, M28b_Q03, M28b_Q04, M28b_Q05_amt, M28b_Q05_curr, M28b_Q06_amt, M28b_Q06_curr, M28b_Q07, M28b_Q08a_amt_gift, M28b_Q08a_curr_gift, M28b_Q08b_amt_trans, M28b_Q08b_curr_trans, M28b_Q08c_amt_inkin, M28b_Q08c_curr_inkin

M29_ITEM.dta
M29_Q02_Item_os, M29_Q03, M29_Q04, M29_Q05_amt, M29_Q05_curr, M29_Q06_amt, M29_Q06_curr, M29_Q07, M29_Q08a_amt_gift, M29_Q08a_curr_gift, M29_Q08b_amt_trans, M29_Q08b_curr_trans, M29_Q08c_amt_inkin, M29_Q08c_curr_inkin

M30_ITEM.dta
M30_Q02_Item_os, M30_Q03, M30_Q04, M30_Q05_amt, M30_Q05_curr, M30_Q06_amt, M30_Q06_curr, M30_Q07, M30_Q08a_amt_gift, M30_Q08a_curr_gift, M30_Q08b_amt_trans, M30_Q08b_curr_trans, M30_Q08c_amt_inkin, M30_Q08c_curr_inkin

M31_ITEM.dta
M31_Q02_Item_os, M31_Q03, M31_Q04, M31_Q05_amt, M31_Q05_curr, M31_Q06_amt, M31_Q06_curr, M31_Q07, M31_Q08a_amt_gift, M31_Q08a_curr_gift, M31_Q08b_amt_trans, M31_Q08b_curr_trans, M31_Q08c_amt_inkin, M31_Q08c_curr_inkin

facility_distance_roster.dta
M4_Q36

social_safety_nets.dta
M20_Q01, M20_Q02, M20_Q03_MONTH, M20_Q03_YEAR, M20_Q04_VALUE, M20_Q04_CURRENCY, M20_Q05, M20_Q06, M20_Q07, M20_Q08, M20_Q09

M22A_Roster_A.dta
M22A_Q02_OS_A, M22A_Q03_A, M22A_Q04_A, M22A_Q05_qty_A, M22A_Q05_unit_A, M22A_Q05_size_A, M22A_Q06_amt_A, M22A_Q06_curr_A, M22A_Q07_qty_A, M22A_Q07_unit_A, M22A_Q07_size_A, M22A_Q08_amt_A, M22A_Q08_curr_A, M22A_Q09_A, M22A_Q10_qty_A, M22A_Q10_unit_A, M22A_Q10_size_A, M22A_Q11_qty_A, M22A_Q11_unit_A, M22A_Q11_size_A, M22A_Q12_qty_A, M22A_Q12_unit_A, M22A_Q12_size_A

M22A_Roster_B.dta
M22A_Q02_OS_B, M22A_Q03_B, M22A_Q04_B, M22A_Q05_qty_B, M22A_Q05_unit_B, M22A_Q05_size_B, M22A_Q06_Bmt_B, M22A_Q06_curr_B, M22A_Q07_qty_B, M22A_Q07_unit_B, M22A_Q07_size_B, M22A_Q08_Bmt_B, M22A_Q08_curr_B, M22A_Q09_B, M22A_Q10_qty_B, M22A_Q10_unit_B, M22A_Q10_size_B, M22A_Q11_qty_B, M22A_Q11_unit_B, M22A_Q11_size_B, M22A_Q12_qty_B, M22A_Q12_unit_B, M22A_Q12_size_B

M22B_Roster_A.dta
M22B_Q01_OS_A, M22B_Q03_qty_A, M22B_Q03_unit_A, M22B_Q03_size_A, M22B_Q04_A, M22B_Q05_qty_A, M22B_Q06_val_A, M22B_Q06_curr_A, M22B_Q07_qty_A, M22B_Q08_qty_A, M22B_Q09_qty_A, M22B_Q10_qty_A

M22B_Roster_B.dta
M22B_Q01_OS_B, M22B_Q03_qty_B, M22B_Q03_unit_B, M22B_Q03_size_B, M22B_Q04_B, M22B_Q05_qty_B, M22B_Q06_val_B, M22B_Q06_curr_B, M22B_Q07_qty_B, M22B_Q08_qty_B, M22B_Q09_qty_B, M22B_Q10_qty_B

M23A_Roster_A.dta
M23A_Q02_OS_A, M23A_Q03_A, M23A_Q04_A, M23A_Q05_qty_A, M23A_Q05_unit_A, M23A_Q05_size_A, M23A_Q06_amt_A, M23A_Q06_curr_A, M23A_Q07_qty_A, M23A_Q07_unit_A, M23A_Q07_size_A, M23A_Q08_amt_A, M23A_Q08_curr_A, M23A_Q09_A, M23A_Q10_qty_A, M23A_Q10_unit_A, M23A_Q10_size_A, M23A_Q11_qty_A, M23A_Q11_unit_A, M23A_Q11_size_A, M23A_Q12_qty_A, M23A_Q12_unit_A, M23A_Q12_size_A

M22B_Roster.dta
M22B_Q01_OS, M22B_Q03_qty, M22B_Q03_unit, M22B_Q03_size, M22B_Q04, M22B_Q05_qty, M22B_Q06_val, M22B_Q06_curr, M22B_Q07_qty, M22B_Q08_qty, M22B_Q09_qty, M22B_Q10_qty

Points_of_purchase.dta
M32_Q01, M32_Q01_oth

M33_domestic.dta
M33_Q7_Amt, M33_Q7_Curr, M33_Q8_Amt, M33_Q8_Curr, M33_Q9_Amt, M33_Q9_Curr, M33_Q10_Amt, M33_Q10_Curr

```

:::

::: {.column width="20%"}

- Link to questionnaire on Designer
- Points to snapshot of version imported into Headquarters

:::

::::

## Export file manifest {.t2}

:::: {.columns}

::: {.column width="80%"}

```{.text code-line-numbers="8-9"}
- TODO: add code block containing text from `export__readme.txt` from "Capturing What Matters"
- TODO: use `code-line-numbers` to walk through code and explain

Generated by Survey Solutions export module 23.06.1 (build 34560) on Saturday, 16 September 2023
The data in this download were collected using the Survey Solutions questionnaire "ZiHBS 2023 Actual Pilot". 
You can open the questionnaire in the Survey Solutions Designer online by that link: https://designer.mysurvey.solutions/questionnaire/details/07a29ec50a0f4b5f9a7f45dd591d2514$2

ZiHBS_2023_Actual_pilot.dta
cp_province, cp_district, cp_ward, cp_sector, cp_ea, cp_region, cp_geocode, cp_area, cp_structure, cp_hhnumber, cp_hhid, cp_hhead, cp_phoneno, cp_address, cp_gps, cp_main, st_supname, st_intname, st_identified, st_HHmove, M1_Q0a, M1_Q0b, M1_start_date, M1_Q01, M1_Q02, M1_Q03, M1_Q04, M1_Q05, M2_START_DATE, M2_Q01, M3_start_date_time, M3_respondent, M3_Q00, M3_Q01, M4_start_date, M4_respondent, M4_Q01, M4_Q01_oth, M4_Q01a, M4_Q01b_Amt, M5_Q01b_Curr, M4_Q01c_Amt, M4_Q01c_Curr, M4_Q02, M4_Q02_oth, M4_Q03, M4_Q03_oth, M4_Q04, M4_Q04_oth, M4_Q05, M4_Q05_oth, M4_Q06, M4_Q07, M4_Q08, M4_Q08_oth, M4_Q09, M4_Q09_oth, M4_Q10, M4_Q10_oth, M4_Q11, M4_Q12, M4_Q13, M4_Q13_oth, M4_Q14, M4_Q14_oth, M4_Q15, M4_Q15_oth, M4_Q16, M4_Q16_oth, M4_Q17, M4_Q18, M4_Q18_oth, M4_Q19, M4_Q19_oth, M4_Q20, M4_Q21, M4_Q22, M4_Q23, M4_Q24, M4_Q24_oth, M4_Q25, M4_Q25_oth, M4_Q26, H27, M4_Q28, M4_Q28_oth, M4_Q29, M4_Q30, M4_Q31, M4_Q32, M4_Q33, M4_Q33_oth, M4_Q34, M4_Q35, M4_Q35_oth, M4_Q37, M4_Q38a_Amt, M4_Q38a_Curr, M4_Q38b_Amt, M4_Q38b_Curr, M4_Q38c_Amt, M4_Q38c_Curr, M5_15d_Amt, M4_Q38d_Curr, M4_Q39, M4_Q40_Amt, M5_Q40b_Curr, M8_start_date_time, M8_respondent, M8_Q01, M9_START_DATE, M10_START_DATE, M10_RESPONDENT, M11_start_date, M11_respondent, M12_start_date, M13_start_date, M14_start_date_time, M14_Q00, M14_Q01, M14_Q0E1, M15_Q02a, M16_StartTime, M16_respondent, M16_Q1a, M16_Q1b, M16_Q1c, M16_Q1d, M16_Q1B2, M16_Q2a, M16_Q2b, M16_Q2c, M16_Q2d, M16_Q2B2, M16_Q3a, M16_Q3b, M16_Q3c, M16_Q3d, M16_Q3B2, M16_Q4a, M16_Q4b, Module17_start_date, Respondent_for_module17, M17_01B, M17_Q01, M18_startDateTime, M18_respondent, M18_Q01, Q18_Q02, M18_Q11_amt, M18_Q11_cuur, M18_Q12, M18_Q13_amt, M18_Q13_cuur, M19_START_DATE, M19_RESPONDENT, M19_Q01, M20_START_DATE, M20_RESPONDENT, M21_Starting_Time, M21_Q01, M21_FAFH, M22A_StartTime, M22A_respondent, M22A_Q02_EXPENDITURE, check_M22A_complete, M22A_Q02_cereals, M22A_Q02_flours, M22A_Q02_bakery, M22A_Q02_BF_cereals, M22A_Q02_pasta, M22A_Q02_OthCreals, M22A_Q02_LiveAnimal, M22A_Q02_Meat_fresh, M22A_Q02_Meat_dried, M22A_Q02_Offal_blood, M22A_Q02_meat_prep, M22A_Q02_Fish_fresh, M22A_Q02_Fish_dried, M22A_Q02_Fish_prep, M22A_Q02_OthSFFresh, M22A_Q02_OtSFDried, M22A_Q02_oth_sf_prep, M22A_Q02_milk_raw, M22A_Q02_MilkSkimm, M22A_Q02_OthMilkCre, M22A_Q02_NonAni_milk, M22A_Q02_Cheese, M22A_Q02_Yoghurt, M22A_Q02_MilkDessert, M22A_Q02_Eggs, M22A_Q02_Vege_oils, M22A_Q02_Butter_fats, M22A_Q02_Margarine, M22A_Q02_Oth_Ani_fat, M22A_Q02_Tropi_fruit, M22A_Q02_CitrusFrt, M22A_Q02_StoneFrut, M22A_Q02_BerriyFresh, M22A_Q02_Oth_fruit_f, M22A_Q02_FrozFruit, M22A_Q02_Fruit_dried, M22A_Q02_Nuts, M22A_Q02_Fr_nut_prep, M22A_Q02_Leafy_veg, M22A_Q02_Fruit_veg, M22A_Q02_Green_leg, M22A_Q02_Ot_veg_tube, M22A_Q02_potatoes, M22A_Q02_Pulses, M22A_Q02_OtVegiDried, M22A_Q02_vegi_froze, M22A_Q02_Vegi_prep, M22A_Q02_Cane_sugar, M22A_Q02_Other_sugar, M22A_Q02_Jams, M22A_Q02_Nut_paste, M22A_Q02_Chocolate, M22A_Q02_Ice_cream, M22A_Q02_gums_candy, M22A_Q02_PrepFood, M22A_Q02_Baby_food, M22A_Q02_Salt_cond, M22A_Q02_Spices, M22A_Q02_juices, M22A_Q02_Coffee, M22A_Q02_tea, M22A_Q02_CocoaDrink, M22A_Q02_Water, M22A_Q02_Soft_drinks, M22A_Q02_OthNonAlcoh, M22B_StartTime, M22B_respondent, M22B_Q01_EXPENDITURE, check_M22B_complete, M22B_Q01_cereals, M22B_Q01_flours, M22B_Q01_bakery, M22B_Q01_BF_cereals, M22B_Q01_pasta, M22B_Q01_OthCreals, M22B_Q01_LiveAnimal, M22B_Q01_Meat_fresh, M22B_Q01_Meat_dried, M22B_Q01_Offal_blood, M22B_Q01_meat_prep, M22B_Q01_Fish_fresh, M22B_Q01_Fish_dried, M22B_Q01_Fish_prep, M22B_Q01_OthSFFresh, M22B_Q01_OtSFDried, M22B_Q01_oth_sf_prep, M22B_Q01_milk_raw, M22B_Q01_MilkSkimm, M22B_Q01_OthMilkCre, M22B_Q01_NonAni_milk, M22B_Q01_Cheese, M22B_Q01_Yoghurt, M22B_Q01_MilkDessert, M22B_Q01_Eggs, M22B_Q01_Vege_oils, M22B_Q01_Butter_fats, M22B_Q01_Margarine, M22B_Q01_Oth_Ani_fat, M22B_Q01_Tropi_fruit, M22B_Q01_CitrusFrt, M22B_Q01_StoneFrut, M22B_Q01_BerriyFresh, M22B_Q01_Oth_fruit_f, M22B_Q01_FrozFruit, M22B_Q01_Fruit_dried, M22B_Q01_Nuts, M22B_Q01_Fr_nut_prep, M22B_Q01_Leafy_veg, M22B_Q01_Fruit_veg, M22B_Q01_Green_leg, M22B_Q01_Ot_veg_tube, M22B_Q01_potatoes, M22B_Q01_Pulses, M22B_Q01_OtVegiDried, M22B_Q01_vegi_froze, M22B_Q01_Vegi_prep, M22B_Q01_Cane_sugar, M22B_Q01_Other_sugar, M22B_Q01_Jams, M22B_Q01_Nut_paste, M22B_Q01_Chocolate, M22B_Q01_Ice_cream, M22B_Q01_gums_candy, M22B_Q01_PrepFood, M22B_Q01_Baby_food, M22B_Q01_Salt_cond, M22B_Q01_Spices, M22B_Q01_juices, M22B_Q01_Coffee, M22B_Q01_tea, M22B_Q01_CocoaDrink, M22B_Q01_Water, M22B_Q01_Soft_drinks, M22B_Q01_OthNonAlcoh, M23A_start_date, M23A_respondent, M23A_Q01, M23A_Q02_check, M23A_Q02_SpiritsLiq, M23A_Q02_WineGrapes, M23A_Q02_CiderPerry, M23A_Q02_Beer, M23A_Q02_Cigarettes, M23A_Q02_Cigars, M23A_Q02_OthTobacco, M23A_Q02_Narcotics, M23B_start_date, M23b_respondent, M23B_Q01, M23B_Q02_check, M23B_Q02_SpiritsLiq, M23B_Q02_WineGrapes, M23B_Q02_CiderPerry, M23B_Q02_Beer, M23B_Q02_Cigarettes, M23B_Q02_Cigars, M23B_Q02_OthTobacco, M23B_Q02_Narcotics, Module24_start_date, Respondent_for_module_24, M24_Q01, M25_start_date, M25_Respondent, M25_Q01, M25b_start_date, M25b_Respondent, M25b_Q01, M26_start_date, M26_Respondent, M26_Q01, M27_start_date, M27_Respondent, M27_Q01, M28a_start_date, M28a_Respondent, M28a_Q01, M28b_start_date, M28b_Respondent, M28b_Q01, M29_start_date, M29_Respondent, M29_Q01, M30_start_date, M30_Respondent, M30_Q01, M31_start_date, M31_Respondent, M31_Q01, M32_START_DATE, M32_RESPONDENT, M32_Q00, M33_Start_Date, M33_respondent, M33_Q1, M33_Q2, M33_Q3, M33_Q4, M33_Q5, M33_Q6, M34_StartTime, M34_respondent, M34_Q1a, M34_Q1b, M34_Q1c, M34_Q1d, M34_Q1e, M34_Q1f, M34_Q1g, M34_Q1h, M35_StartTime, M35_respondent, M35_Q01, M35_Q02, M35_Q03, M35_Q04, M35_Q05, M35_Q06, M35_Q07, M35_Q08, M35_Q09, M35_Q10, M35_Q11, M35_Q12, M35_Q13, M35_Q14, M35_Q15, M36_Q01a, M36_Q02a1, M36_Q02_1, M36_Q01b, M36_Q02a2, M36_Q02_2, M36_Q01c, M36_Q02a3, M36_Q02_3, M36_Q03, M36_Q04a, M36_Q04b, M36_Q04c, M36_Q04c_oth

hhmembers.dta
M2_Q02, M2_Q03, M2_Q04, M2_Q05, M2_Q06, M2_Q07, M2_Q08, M2_Q09, M2_Q10, M2_Q11, M2_Q12, M2_Q13, M2_Q14, M2_Q14_OTH, M2_Q15, M2_Q16, M2_Q17, M2_Q18, M2_Q19, M2_Q20, M2_Q21, M2_Q21_ISCO, M2_Q22, M2_Q23, M2_Q24, M2_Q25, M2_Q26, M2_Q26_ISIC, M2_Q27, M2_Q28, M2_Q29_auth, M2_Q29, M9_Q0respondent, M9_RES_ID, M9_Q01, M9_Q02, M2_Q02_oth, M9_Q03, M9_Q03a, M9_Q04, M9_Q05, M9_Q06, M2_Q06_oth, M9_Q07, M9_Q07_oth, M9_Q08, M9_Q09, M9_Q10, M9_Q11, M9_Q11_oth, M9_Q12, M9_Q13_amt, M9_Q13_curr, M9_Q14, M9_Q15, M9_Q16_AMT, M9_Q16_curr, M9_Q17, M9_Q18_AMT, M9_Q18_Curr, M9_Q19, M9_Q20, M9_Q21_AMT, M9_Q21_Curr, M9_Q22, M9_Q22_oth, M9_Q23, M9_Q24, M10_Q0respondent, M10_RES_ID, M10_Q01, M10_Q02, M10_Q03, M10_Q04, M10_Q06, M10_Q07, M10_Q08, M10_Q09, M10_Q10, M10_Q11, M10_Q12, M10_Q13, M10_Q14, M10_Q14_oth, M10_Q15, M10_Q15_oth, M10_Q16, M10_Q17, M10_Q17ISCO, M10_Q18, M10_Q18_ISIC, M10_Q19, M10_Q20, M10_Q21, M10_Q22, M10_Q23, M10_Q23_oth, M10_Q24, M10_Q25, M10_Q26, M10_Q27, M10_Q28, M10_Q28_ISCO, M10_Q29, M10_Q29_ISIC, M11_Q0respondent, M11_RES_ID, M11_Q01, M11_Q02, M11_Q02_oth, M11_Q03, M11_Q03_oth, M11_Q04, M11_Q04_oth, M11_Q05, M11_Q05_oth, M11_Q06, M11_Q07, M11_Q07_oth, M11_Q08, M11_Q09, M11_Q10, M11_Q10_oth, M11_Q11, M11_Q12, M11_Q13, M11_Q14, M11_Q15, M11_Q16, M11_Q16_oth, M12_Q0respondent, M12_RES_ID, M12_Q01, M12_Q02, M12_Q03, M12_Q04, M12_Q05, M12_Q06, M12_Q07a, M12_Q7a_oth, M12_Q07b, M12_Q07b_oth, M12_Q07c, M12_Q07c_oth, M12_Q07d, M12_Q07d_oth, M12_Q07e, M12_Q07e_oth, M12_Q07f, M12_Q07f_oth, M12_Q08, M12_Q08_oth, M12_Q09, M13_Q0respondent, M13_RES_ID, M13_Q01, M13_Q02, M13_Q03, M13_Q04_curr, M13_Q04_amt_ZWD, M13_Q04_amt_USD, M13_Q04_amt_RAND, M13_Q04_amt_PULA, M13_Q05, M13_Q06, M13_Q07_curr, M13_Q07_amt, M13_Q08_curr, M13_Q08_amt, M13_Q09_amt, M13_Q09_curr, M13_Q10, M13_Q11_amt, M13_Q11_curr, M13_Q12, M13_Q13_amt, M13_Q13_Curr, M13_Q14, M13_Q15_amt, M13_Q15_curr, M13_Q16, M13_Q17_Amt, M13_Q17_Curr, M13_Q18

International_Migration.dta
M3_Q02, M3_Q03, M3_Q04, M3_Q05, M3_Q06, M3_Q07, M3_Q08, M3_Q09, M3_Q10, M3_Q11, M3_Q12, M3_Q13A, M3_Q13B, M3_Q14, M3_Q15, M3_Q16_amt, M3_Q16_curr, M3_Q17_amt, M3_Q18_curr

hh_assets_roster.dta
M8_Q02, M8_Q03, M8_Q04, M8_Q05_amt, M8_Q05_curr, M8_Q06, M8_Q07_amt, M8_Q07_curr

nfe_roster.dta
M15_Q02_b, M15_Q03, M15_Q04, M15_Q05, M15_Q05_oth, M15_Q06, M15_Q07, M15_Q08_amt, M15_Q08_curr, M15_Q09_amt, M15_Q09_curr, M15_Q10_amt, M15_Q10_curr, M15_Q11_a_amt, M15_Q11_a_curr, M15_Q11_b_amt, M15_Q11_b_curr, M15_Q11_c_amt, M15_Q11_c_curr, M15_Q11_d_amt, M15_Q11_d_curr, M15_Q11_e_amt, M15_Q11_e_curr, M15_Q11_f_amt, M15_Q11_f_curr, M15_Q11_g_amt, M15_Q11_g_curr, M15_Q11_h_amt, M15_Q11_h_curr, M15_Q11_j_amt, M15_Q11_j_curr, M15_Q11_k_amt, M15_Q11_k_curr, M15_Q11_l_amt, M15_Q11_l_curr, M15_Q11_m_amt, M15_Q11_m_curr, M15_Q11_n_amt, M15_Q11_n_curr, M15_Q11_o_amt, M15_Q11_o_curr, M15_Q11_o, M15_Q11_p_amt, M15_Q11_p_curr

Mod17_Crops.dta
M17_Q02b, M17_Q02, M17_Q02_UNIT, M17_Q03, M17_Q04, M17_Q05, M17_Q05_oth, M17_Q06_QTY, M17_Q06_UNIT, M17_Q07, M17_Q07_CURRENCY, M17_Q08, M17_Q09, M17_Q09_CURRENCY, M17_Q10, M17_Q10_CURRENCY, M17_Q11, M17_Q11_oth, M17_Q12, M17_Q13, M17_Q14, M17_Q15, M17_Q15_CURRENCY, M17_Q16, M17_Q17, M17_Q17_CURRENCY, M17_Q18, M17_Q19, M17_Q19_CURRENCY, M17_Q20, M17_Q21, M17_Q21_CURRENCY, M17_Q22, M17_Q23, M17_Q24, M17_Q24_CURRENCY, M17_Q25

livestock.dta
M18_Q02_oth, M18_Q03, Q18_Q04, M18_Q05_amt, M18_Q05_cuur, M18_Q06, M18_Q07, M18_Q08_amt, M18_Q08_curr, M18_Q09, M18_Q10

M19_LABOUR_INCOME_Roster.dta
M19_Q02_curr, M19_Q02_amt_ZWD, M19_Q02_amt_USD, M19_Q02_amt_RAND, M19_Q02_amt_PULA

FAFH_roster.dta
M21_Q02_amt, M21_Q02_curr, M21_Q03

M24_Q07_gifts.dta
M24_Q02_ItemList

M25_Product.dta
M25_Q02_ItemList

M25b_Product.dta
M25b_Q02_ItemList

M26_Product.dta
M26_Q02_ItemList

M27_Product.dta
M27_Q02_ItemList

M28a_Product.dta
M28a_Q02_ItemList

M28b_Product.dta
M28b_Q02_ItemList

M29_Product.dta
M29_Q02_ItemList

M30_Product.dta
M30_Q02_ItemList

M31_Product.dta
M31_Q02_ItemList

Commodities_non_food_1mon.dta
M24_Q02_Item_os, M24_Q03, M24_Q04, M24_Q05_amt, M24_Q05_curr, M24_Q06_amt, M24_Q06_curr, M24_Q07, M24_Q08a_amt_gift, M24_Q08a_curr_gift, M24_Q08b_amt_trans, M24_Q08b_curr_trans, M24_Q08c_amt_inkin, M24_Q08c_curr_inkin

M25_ITEM.dta
M25_Q02_Item_os, M25_Q03, M25_Q04, M25_Q05_amt, M25_Q05_curr, M25_Q06_amt, M25_Q06_curr, M25_Q07, M25_Q08a_amt_gift, M25_Q08a_curr_gift, M25_Q08b_amt_trans, M25_Q08b_curr_trans, M25_Q08c_amt_inkin, M25_Q08c_curr_inkin

M25b_ITEM.dta
M25b_Q02_Item_os, M25b_Q03, M25b_Q04, M25b_Q05_amt, M25b_Q05_curr, M25b_Q06_amt, M25b_Q06_curr, M25b_Q07, M25b_Q08a_amt_gift, M25b_Q08a_curr_gift, M25b_Q08b_amt_trans, M25b_Q08b_curr_trans, M25b_Q08c_amt_inkin, M25b_Q08c_curr_inkin

M26_ITEM.dta
M26_Q02_Item_os, M26_Q03, M26_Q04, M26_Q05_amt, M26_Q05_curr, M26_Q06_amt, M26_Q06_curr, M26_Q07, M26_Q08a_amt_gift, M26_Q08a_curr_gift, M26_Q08b_amt_trans, M26_Q08b_curr_trans, M26_Q08c_amt_inkin, M26_Q08c_curr_inkin

M27_ITEM.dta
M27_Q02_Item_os, M27_Q03, M27_Q04, M27_Q05_amt, M27_Q05_curr, M27_Q06_amt, M27_Q06_curr, M27_Q07, M27_Q08a_amt_gift, M27_Q08a_curr_gift, M27_Q08b_amt_trans, M27_Q08b_curr_trans, M27_Q08c_amt_inkin, M27_Q08c_curr_inkin

M28a_ITEM.dta
M28a_Q02_Item_os, M28a_Q03, M28a_Q04, M28a_Q05_amt, M28a_Q05_curr, M28a_Q06_amt, M28a_Q06_curr, M28a_Q07, M28a_Q08a_amt_gift, M28a_Q08a_curr_gift, M28a_Q08b_amt_trans, M28a_Q08b_curr_trans, M28a_Q08c_amt_inkin, M28a_Q08c_curr_inkin

M28b_ITEM.dta
M28b_Q02_Item_os, M28b_Q03, M28b_Q04, M28b_Q05_amt, M28b_Q05_curr, M28b_Q06_amt, M28b_Q06_curr, M28b_Q07, M28b_Q08a_amt_gift, M28b_Q08a_curr_gift, M28b_Q08b_amt_trans, M28b_Q08b_curr_trans, M28b_Q08c_amt_inkin, M28b_Q08c_curr_inkin

M29_ITEM.dta
M29_Q02_Item_os, M29_Q03, M29_Q04, M29_Q05_amt, M29_Q05_curr, M29_Q06_amt, M29_Q06_curr, M29_Q07, M29_Q08a_amt_gift, M29_Q08a_curr_gift, M29_Q08b_amt_trans, M29_Q08b_curr_trans, M29_Q08c_amt_inkin, M29_Q08c_curr_inkin

M30_ITEM.dta
M30_Q02_Item_os, M30_Q03, M30_Q04, M30_Q05_amt, M30_Q05_curr, M30_Q06_amt, M30_Q06_curr, M30_Q07, M30_Q08a_amt_gift, M30_Q08a_curr_gift, M30_Q08b_amt_trans, M30_Q08b_curr_trans, M30_Q08c_amt_inkin, M30_Q08c_curr_inkin

M31_ITEM.dta
M31_Q02_Item_os, M31_Q03, M31_Q04, M31_Q05_amt, M31_Q05_curr, M31_Q06_amt, M31_Q06_curr, M31_Q07, M31_Q08a_amt_gift, M31_Q08a_curr_gift, M31_Q08b_amt_trans, M31_Q08b_curr_trans, M31_Q08c_amt_inkin, M31_Q08c_curr_inkin

facility_distance_roster.dta
M4_Q36

social_safety_nets.dta
M20_Q01, M20_Q02, M20_Q03_MONTH, M20_Q03_YEAR, M20_Q04_VALUE, M20_Q04_CURRENCY, M20_Q05, M20_Q06, M20_Q07, M20_Q08, M20_Q09

M22A_Roster_A.dta
M22A_Q02_OS_A, M22A_Q03_A, M22A_Q04_A, M22A_Q05_qty_A, M22A_Q05_unit_A, M22A_Q05_size_A, M22A_Q06_amt_A, M22A_Q06_curr_A, M22A_Q07_qty_A, M22A_Q07_unit_A, M22A_Q07_size_A, M22A_Q08_amt_A, M22A_Q08_curr_A, M22A_Q09_A, M22A_Q10_qty_A, M22A_Q10_unit_A, M22A_Q10_size_A, M22A_Q11_qty_A, M22A_Q11_unit_A, M22A_Q11_size_A, M22A_Q12_qty_A, M22A_Q12_unit_A, M22A_Q12_size_A

M22A_Roster_B.dta
M22A_Q02_OS_B, M22A_Q03_B, M22A_Q04_B, M22A_Q05_qty_B, M22A_Q05_unit_B, M22A_Q05_size_B, M22A_Q06_Bmt_B, M22A_Q06_curr_B, M22A_Q07_qty_B, M22A_Q07_unit_B, M22A_Q07_size_B, M22A_Q08_Bmt_B, M22A_Q08_curr_B, M22A_Q09_B, M22A_Q10_qty_B, M22A_Q10_unit_B, M22A_Q10_size_B, M22A_Q11_qty_B, M22A_Q11_unit_B, M22A_Q11_size_B, M22A_Q12_qty_B, M22A_Q12_unit_B, M22A_Q12_size_B

M22B_Roster_A.dta
M22B_Q01_OS_A, M22B_Q03_qty_A, M22B_Q03_unit_A, M22B_Q03_size_A, M22B_Q04_A, M22B_Q05_qty_A, M22B_Q06_val_A, M22B_Q06_curr_A, M22B_Q07_qty_A, M22B_Q08_qty_A, M22B_Q09_qty_A, M22B_Q10_qty_A

M22B_Roster_B.dta
M22B_Q01_OS_B, M22B_Q03_qty_B, M22B_Q03_unit_B, M22B_Q03_size_B, M22B_Q04_B, M22B_Q05_qty_B, M22B_Q06_val_B, M22B_Q06_curr_B, M22B_Q07_qty_B, M22B_Q08_qty_B, M22B_Q09_qty_B, M22B_Q10_qty_B

M23A_Roster_A.dta
M23A_Q02_OS_A, M23A_Q03_A, M23A_Q04_A, M23A_Q05_qty_A, M23A_Q05_unit_A, M23A_Q05_size_A, M23A_Q06_amt_A, M23A_Q06_curr_A, M23A_Q07_qty_A, M23A_Q07_unit_A, M23A_Q07_size_A, M23A_Q08_amt_A, M23A_Q08_curr_A, M23A_Q09_A, M23A_Q10_qty_A, M23A_Q10_unit_A, M23A_Q10_size_A, M23A_Q11_qty_A, M23A_Q11_unit_A, M23A_Q11_size_A, M23A_Q12_qty_A, M23A_Q12_unit_A, M23A_Q12_size_A

M22B_Roster.dta
M22B_Q01_OS, M22B_Q03_qty, M22B_Q03_unit, M22B_Q03_size, M22B_Q04, M22B_Q05_qty, M22B_Q06_val, M22B_Q06_curr, M22B_Q07_qty, M22B_Q08_qty, M22B_Q09_qty, M22B_Q10_qty

Points_of_purchase.dta
M32_Q01, M32_Q01_oth

M33_domestic.dta
M33_Q7_Amt, M33_Q7_Curr, M33_Q8_Amt, M33_Q8_Curr, M33_Q9_Amt, M33_Q9_Curr, M33_Q10_Amt, M33_Q10_Curr

```

:::

::: {.column width="20%"}

- Each lines represents an exported data file
- First line: name of the file
- Second line: list of columns in the file

:::

::::

## Questionnaire information {.t2}


```{.text code-line-numbers="16-21"}
TODO: files exported for "Capturing What Matters"

├── assignment__actions.dta
├── Commodities_non_food_1mon.dta
├── export__readme.txt
├── facility_distance_roster.dta
├── FAFH_roster.dta
├── hhmembers.dta
├── hh_assets_roster.dta
├── International_Migration.dta
├── interview__actions.dta
├── interview__comments.dta
├── interview__diagnostics.dta
├── interview__errors.dta
├── livestock.dta
├── Questionnaire
│   ├── Categories
│   ├── content.zip
│   ├── ddi.xml
│   ├── document.json
│   └── Preview
├── social_safety_nets.dta
└── ZiHBS_2023_Actual_pilot.dta
```

## Questionnaire preview {.t2}

:::: {.columns}

::: {.column width="30%"}

```{.text code-line-numbers="16,21-22"}
TODO: files exported for "Capturing What Matters"

├── assignment__actions.dta
├── Commodities_non_food_1mon.dta
├── export__readme.txt
├── facility_distance_roster.dta
├── FAFH_roster.dta
├── hhmembers.dta
├── hh_assets_roster.dta
├── International_Migration.dta
├── interview__actions.dta
├── interview__comments.dta
├── interview__diagnostics.dta
├── interview__errors.dta
├── livestock.dta
├── Questionnaire
│   ├── Categories
│   ├── content.zip
│   ├── ddi.xml
│   ├── document.json
│   └── Preview
│       └── Original ZiHBS_2023_Actual_pilot.html
├── social_safety_nets.dta
└── ZiHBS_2023_Actual_pilot.dta
```

:::

::: {.column width="70%"}

TODO: image of HTML document; basically, thumbnail of video to follow

:::


::::

## Questionnaire preview {.t2}

:::: {.columns}

::: {.column width="70%"}

TODO: replace with video that gives short overview of HTML questionnaire doc for "Capturing What Matters". See [here](review_zim_course/slides_not_on_zim_site/19_get_use_data.html#/questionnairepreview.html) 

:::

::: {.column width="30%"}

- Questionnaire metadata
- Data dictionary
    - Variable
    - Type
    - Label/question text
    - Values
- Contains conditions
    - Enablement
    - Validation

:::

::::

## Data documentation {.t2}

:::: {.columns}

::: {.column width="30%"}

```{.text code-line-numbers="19"}
TODO: files exported for "Capturing What Matters"

├── assignment__actions.dta
├── Commodities_non_food_1mon.dta
├── export__readme.txt
├── facility_distance_roster.dta
├── FAFH_roster.dta
├── hhmembers.dta
├── hh_assets_roster.dta
├── International_Migration.dta
├── interview__actions.dta
├── interview__comments.dta
├── interview__diagnostics.dta
├── interview__errors.dta
├── livestock.dta
├── Questionnaire
│   ├── Categories
│   ├── content.zip
│   ├── ddi.xml
│   ├── document.json
│   └── Preview
├── social_safety_nets.dta
└── ZiHBS_2023_Actual_pilot.dta
```

:::

::: {.column width="70%"}

TODO: replace with contents of ddi.xml for "Capturing What Matters" as XML code block

:::


::::

## Data documentation {.t2}

:::: {.columns}

::: {.column width="70%"}

TODO: replace with contents of ddi.xml for "Capturing What Matters" as XML code block

:::

::: {.column width="30%"}

- Use data documentation
- Import into [Nesstar](http://www.ihsn.org/software/ddi-metadata-editor)
- Publish to [NADA](http://nada.ihsn.org/)

:::

::::

## Survey microdata data {.t2}

<!-- An establishing shot -->

```{.text code-line-numbers="3-4,6-15,17-18"}
TODO: files exported for "Capturing What Matters"

├── assignment__actions.dta
├── Commodities_non_food_1mon.dta
├── export__readme.txt
├── facility_distance_roster.dta
├── FAFH_roster.dta
├── hhmembers.dta
├── hh_assets_roster.dta
├── International_Migration.dta
├── interview__actions.dta
├── interview__comments.dta
├── interview__diagnostics.dta
├── interview__errors.dta
├── livestock.dta
├── Questionnaire
├── social_safety_nets.dta
└── ZiHBS_2023_Actual_pilot.dta
```

# Files `r fontawesome::fa(name = "arrow-right-arrow-left")` questionnaire {background-color=var(--s2)}

## Overview {.t2}

:::: {.columns}

::: {.column width="50%"}

```{.text code-line-numbers="3-4,6-15,17-18"}
TODO: files exported for "Capturing What Matters"

├── assignment__actions.dta
├── Commodities_non_food_1mon.dta
├── export__readme.txt
├── facility_distance_roster.dta
├── FAFH_roster.dta
├── hhmembers.dta
├── hh_assets_roster.dta
├── International_Migration.dta
├── interview__actions.dta
├── interview__comments.dta
├── interview__diagnostics.dta
├── interview__errors.dta
├── livestock.dta
├── Questionnaire
├── social_safety_nets.dta
└── ZiHBS_2023_Actual_pilot.dta
```
:::

::: {.column width="50%"}

TODO: replace with image of "Capturing What Matters" in Designer similar to this: review_zim_course/slides_not_on_zim_site/19_get_use_data.html#/link-between-data-questionnaire

:::

::::

## Main data {.t2}

:::: {.columns}

::: {.column width="30%"}

```{.text code-line-numbers="18"}
TODO: files exported for "Capturing What Matters"

├── assignment__actions.dta
├── Commodities_non_food_1mon.dta
├── export__readme.txt
├── facility_distance_roster.dta
├── FAFH_roster.dta
├── hhmembers.dta
├── hh_assets_roster.dta
├── International_Migration.dta
├── interview__actions.dta
├── interview__comments.dta
├── interview__diagnostics.dta
├── interview__errors.dta
├── livestock.dta
├── Questionnaire
├── social_safety_nets.dta
└── ZiHBS_2023_Actual_pilot.dta
```

:::

::: {.column width="70%"}

TODO: video showing

- Open settings
- Show questionnaire variable

:::

::::

<!-- roster file -->

## Roster {.t2}

:::: {.columns}

::: {.column width="30%"}

```{.text code-line-numbers="8"}
TODO: files exported for "Capturing What Matters"

├── assignment__actions.dta
├── Commodities_non_food_1mon.dta
├── export__readme.txt
├── facility_distance_roster.dta
├── FAFH_roster.dta
├── hhmembers.dta
├── hh_assets_roster.dta
├── International_Migration.dta
├── interview__actions.dta
├── interview__comments.dta
├── interview__diagnostics.dta
├── interview__errors.dta
├── livestock.dta
├── Questionnaire
├── social_safety_nets.dta
└── ZiHBS_2023_Actual_pilot.dta
```

:::

::: {.column width="70%"}

TODO: video showing

- Navigate to a roster
- Show roster variable name
- Repeat for 1-2 more rosters

:::

::::

<!-- establishing shot for system-generated files -->

## Survey metadata {.t2}

```{.text code-line-numbers="3,11-14"}
TODO: files exported for "Capturing What Matters"

├── assignment__actions.dta
├── Commodities_non_food_1mon.dta
├── export__readme.txt
├── facility_distance_roster.dta
├── FAFH_roster.dta
├── hhmembers.dta
├── hh_assets_roster.dta
├── International_Migration.dta
├── interview__actions.dta
├── interview__comments.dta
├── interview__diagnostics.dta
├── interview__errors.dta
├── livestock.dta
├── Questionnaire
├── social_safety_nets.dta
└── ZiHBS_2023_Actual_pilot.dta
```

<!-- assignment__actions -->

## Assignments {.t2}

:::: {.columns}

::: {.column width="30%"}

```{.text code-line-numbers="3"}
TODO: files exported for "Capturing What Matters"

├── assignment__actions.dta
├── Commodities_non_food_1mon.dta
├── export__readme.txt
├── facility_distance_roster.dta
├── FAFH_roster.dta
├── hhmembers.dta
├── hh_assets_roster.dta
├── International_Migration.dta
├── interview__actions.dta
├── interview__comments.dta
├── interview__diagnostics.dta
├── interview__errors.dta
├── livestock.dta
├── Questionnaire
├── social_safety_nets.dta
└── ZiHBS_2023_Actual_pilot.dta
```


:::

::: {.column width="70%"}

TODO: video of:

- Navigate to assignments
- Click on assignment ID
- Show history of that assignment

:::

::::

<!-- interview__diagnostics -->

## Interview metadata {.t2}

:::: {.columns}

::: {.column width="30%"}

```{.text code-line-numbers="13"}
TODO: files exported for "Capturing What Matters"

├── assignment__actions.dta
├── Commodities_non_food_1mon.dta
├── export__readme.txt
├── facility_distance_roster.dta
├── FAFH_roster.dta
├── hhmembers.dta
├── hh_assets_roster.dta
├── International_Migration.dta
├── interview__actions.dta
├── interview__comments.dta
├── interview__diagnostics.dta
├── interview__errors.dta
├── livestock.dta
├── Questionnaire
├── social_safety_nets.dta
└── ZiHBS_2023_Actual_pilot.dta
```

:::

::: {.column width="70%"}

TODO: video of:

- Navigate to interviews tab
- Show attributes of all interviews

:::

::::

<!-- interview__actions -->

## Interview transaction history {.t2}

:::: {.columns}

::: {.column width="30%"}

```{.text code-line-numbers="11"}
TODO: files exported for "Capturing What Matters"

├── assignment__actions.dta
├── Commodities_non_food_1mon.dta
├── export__readme.txt
├── facility_distance_roster.dta
├── FAFH_roster.dta
├── hhmembers.dta
├── hh_assets_roster.dta
├── International_Migration.dta
├── interview__actions.dta
├── interview__comments.dta
├── interview__diagnostics.dta
├── interview__errors.dta
├── livestock.dta
├── Questionnaire
├── social_safety_nets.dta
└── ZiHBS_2023_Actual_pilot.dta
```

:::

::: {.column width="70%"}

TODO: video of:

- Navigate to interviews
- Click on assignment ID
- Show history of that interview

:::

::::

<!-- interview__comments -->

## Comments {.t2}

:::: {.columns}

::: {.column width="30%"}

```{.text code-line-numbers="12"}
TODO: files exported for "Capturing What Matters"

├── assignment__actions.dta
├── Commodities_non_food_1mon.dta
├── export__readme.txt
├── facility_distance_roster.dta
├── FAFH_roster.dta
├── hhmembers.dta
├── hh_assets_roster.dta
├── International_Migration.dta
├── interview__actions.dta
├── interview__comments.dta
├── interview__diagnostics.dta
├── interview__errors.dta
├── livestock.dta
├── Questionnaire
├── social_safety_nets.dta
└── ZiHBS_2023_Actual_pilot.dta
```

:::

::: {.column width="70%"}

TODO: video of:

- (Navigate to interviews)
- Click on interview
- Show comments question-and interview-level comments

:::

::::

<!-- interview__errors -->

## Validation errors {.t2}

:::: {.columns}

::: {.column width="30%"}

```{.text code-line-numbers="14"}
TODO: files exported for "Capturing What Matters"

├── assignment__actions.dta
├── Commodities_non_food_1mon.dta
├── export__readme.txt
├── facility_distance_roster.dta
├── FAFH_roster.dta
├── hhmembers.dta
├── hh_assets_roster.dta
├── International_Migration.dta
├── interview__actions.dta
├── interview__comments.dta
├── interview__diagnostics.dta
├── interview__errors.dta
├── livestock.dta
├── Questionnaire
├── social_safety_nets.dta
└── ZiHBS_2023_Actual_pilot.dta
```

:::

::: {.column width="70%"}

TODO: video of:

- (Navigate to interviews)
- Click on interview
- Show either validation question-level errors or list of questions with errors on Complete screen

:::

::::


# Variables `r fontawesome::fa(name = "arrow-right-arrow-left")` questionnaire {background-color=var(--s2)}

## Same name in data as in Designer ... {.t2}

:::: {.columns}

::: {.column width="50%"}

TODO: image of Designer

:::

::: {.column width="50%"}

TODO: table with variable in focus and a few fake observations

:::

::::

## ... with some exceptions {.t2}

::: {.panel-tabset}

### List `r fontawesome::fa(name = "list")`

:::: {.columns}

::: {.column width="50%"}
TODO: image of Designer
:::

::: {.column width="50%"}

```{r}
#| eval: true
list_var <- data.frame(
    var__0 = c("First", "Premier", "Primero"),
    var__1 = c("Second", "Second", "Segundo"),
    var__2 = c("Third", "Troisième", "Tercero"),
    var__3 = c("Fourth", "##N/A##", "Tercero"),
    var__4 = c("Fifth", "##N/A##", "Cuarto"),
    var__5 = c("Sixth", "##N/A##", "##N/A##"),
    var__6 = c("Seventh", "##N/A##", "##N/A##")
)

reactable::reactable(
    data = list_var,
    striped = TRUE,
    defaultColDef = reactable::colDef(minWidth = 200),
    theme = s2_theme
)

```

`r fontawesome::fa(name = "lightbulb")` Learn more [here](https://support.mysurvey.solutions/questionnaire-designer/questions/list-question/).

:::

::::

### Multi-select `r fontawesome::fa(name = "list-check")`

:::: {.columns}

::: {.column width="50%"}
TODO: image of Designer
:::

::: {.column width="50%"}

TODO: table with variable in focus and a few fake observations

var__1, var__2, ... , var__N

`r fontawesome::fa(name = "lightbulb")` Learn more [here](https://support.mysurvey.solutions/questionnaire-designer/questions/categorical-multi-select-question/).

:::

::::

### GPS `r fontawesome::fa(name = "location-dot")`

:::: {.columns}

::: {.column width="50%"}
TODO: image of Designer
:::

::: {.column width="50%"}

TODO: table with variable in focus and a few fake observations

gps__Latitude, gps__Longitude, gps__Accuracy, gps__Altitude, gps__Timestamp

`r fontawesome::fa(name = "lightbulb")` Learn more [here](https://support.mysurvey.solutions/questionnaire-designer/questions/gps-question/).

:::

::::

### Geography `r fontawesome::fa(name = "draw-polygon")`

:::: {.columns}

::: {.column width="50%"}
TODO: image of Designer
:::

::: {.column width="50%"}

TODO: table with variable in focus and a few fake observations

geo
<!-- sequence of coordinates of each recorded point in the string format “lg,lt;lg,lt;….;lg,lt”, where lg is the longitude and lt is the latitude of each point, a decimal dot is always used for fractional values; -->
geo__area
geo__len
geo__num
geo__racc
geo__rfrq

For simplicity, showing area

`r fontawesome::fa(name = "lightbulb")` Learn more [here](https://docs.mysurvey.solutions/questionnaire-designer/questions/geography-question/).

:::

::::

:::

# Identifiers `r fontawesome::fa(name = "id-card")` {background-color=var(--s2)}

## Identifiers {.t2}

:::: {.columns}

::: {.column width="70%"}

```{r}
#| label: ID variable table
#| eval: true

id_vars <- data.frame(
    interview__id = uuid::UUIDgenerate(n = 4),
    interview__key = create_keys(n = 4)
)

id_vars_tbl <- reactable::reactable(
    data = id_vars,
    striped = TRUE,
    columns = list(
        interview__id = reactable::colDef(minWidth = 350),
        interview__key = reactable::colDef(minWidth = 125)
    ),
    theme = s2_theme
)

id_vars_tbl

```

:::

::: {.column width="30%"}

- `interview__key`. Human-facing ID
- `interview__id`. Computer-facing ID
- See more [here](https://docs.mysurvey.solutions/headquarters/export/identify_records/)

:::

::::

## interview\_\_key {.t2}

:::: {.columns}

::: {.column width="70%"}

TODO: image of case on the tablet (without sensitive PII)

:::

::: {.column width="30%"}

- What the interviewer sees

:::

::::

## interview\_\_key {.t2}

:::: {.columns}

::: {.column width="70%"}

TODO: image/video of case or searching on the HQ/Supervisor

:::

::: {.column width="30%"}

- What the interviewer sees
- How survey manager can search

:::

::::

## interview\_\_id {.t2}

:::: {.columns}

::: {.column width="70%"}

```{r}
#| label: single interview__key
#| eval: true

id_vars_tbl
```

:::

::: {.column width="30%"}

- How identified in export

:::

::::


## interview\_\_id {.t2}

:::: {.columns}

::: {.column width="70%"}

TODO: composite image of URL and API param, where `interview__id` component highlighted in each

Or two images of both

:::

::: {.column width="30%"}

- How identified in export
- How referenced in the system

:::

::::

## Roster IDs {.t2}

:::: {.columns}

::: {.column width="33%"}

```{.text code-line-numbers="8"}
TODO: files exported for "Capturing What Matters"

├── assignment__actions.dta
├── Commodities_non_food_1mon.dta
├── export__readme.txt
├── facility_distance_roster.dta
├── FAFH_roster.dta
├── hhmembers.dta
├── hh_assets_roster.dta
├── International_Migration.dta
├── interview__actions.dta
├── interview__comments.dta
├── interview__diagnostics.dta
├── interview__errors.dta
├── livestock.dta
├── Questionnaire
│   ├── Categories
│   ├── content.zip
│   ├── ddi.xml
│   ├── document.json
│   └── Preview
├── social_safety_nets.dta
└── ZiHBS_2023_Actual_pilot.dta
```

:::

::: {.column width="33%"}

```{r}
#| label: roster in data viewer 
#| eval: true

# create realistic roster data
roster_vars <- data.frame(
    interview__key = c(rep(create_key(), 3), rep(create_key(), 2)),
    hhmembers__id = c(1, 2, 3, 1, 2)
)

reactable::reactable(
    data = roster_vars,
    defaultColDef = reactable::colDef(minWidth = 100),
    theme = s2_theme
)
```

TODO: adapt variable name to "Capturing What Matters" roster name

:::

::: {.column width="33%"}

- Name of file + `__id`
- Value depends on roster type

:::

::::

# Missing values `r fontawesome::fa(name = "notdef")` {background-color=var(--s2)}

## Missing values (in Stata) {.t2}

:::: {.columns}

::: {.column width="70%"}

```{r}
#| label: missing value examples
#| eval: true

# create fake data
df_w_miss <- data.frame(
    names = c("Hello", "##N/A##", "Goodbye", "Jambo"),
    yes_no = c("1", "0", ".a", 1),
    number = c("50", ".", ".a", "-999999999")
)

reactable::reactable(
    data = df_w_miss,
    defaultColDef = reactable::colDef(minWidth = 100),
    theme = s2_theme
)
```

:::

::: {.column width="30%"}

- Answered
- Disabled
- Unanswerd

:::

::::


## Missing values (in Stata) {.t2}

TODO: confirm info in table is correct

```{r}
#| eval: true
missing_markers <- tibble::tribble(
    ~type,          ~disabled,  ~unanswered,
    "String",       '""',       "##N/A##", 
    "Numeric",      ".",        "-999999999",
    "Categorical",  ".",        ".a"
)

reactable::reactable(
    data = missing_markers,
    defaultColDef = reactable::colDef(minWidth = 100),
    columns = list(
        type = reactable::colDef(name = "Variable type"),
        disabled = reactable::colDef(name = "Disabled"),
        unanswered = reactable::colDef(name = "Unanswered")
    ),
    theme = s2_theme
)

# missing_markers |>
#     gt::gt() |>
#     gt::cols_label(
#         type = "Variable type",
#         disabled = "Disabled",
#         unanswered = "Unanswered"
#     )
```


# Use data {background-color=var(--s3)}

## Merge {.t3}

TODO: sketch data model as [here](https://dm.cynkra.com/articles/howto-dm-theory.html#model)

```{r}

frame <- data.frame(
   interview__id = uuid::UUIDgenerate(n = 2),
   interview__key = create_keys(n = 2) 
)

hholds <- frame

# members <- 

```

<!-- 

# create dm object as if a list with:
dm_obj <- dm::dm(df1, df2, df3)

# add primary keys like this:
dm_obj <- dm_obj |>
    dm::dm_add_pk(table = df1, columns = c(id1, id2)),
    dm::dm_add_pk(table = df2, columns = c(id1, id2)),

# add foreign key

 -->

## Merge {.t3}

:::: {.columns}

::: {.column width="50%"}

### Data

::: {.panel-tabset}

### Households `r fontawesome::fa(name = "house")`

TODO: show household df

### People `r fontawesome::fa(name = "users")`

TODO: show person df

:::

:::

::: {.column width="50%"}

### Merge

TODO: code for merging

:::

::::

## Merge with Stata {.t3}

TODO: Arthur to provide

## Merge with SPSS {.t3}

TODO: Victor to provide code

## Merge with R {.t3}

TODO: Arthur to provide (with tidyverse)
