---
format: 
    revealjs: 
        theme: [default, ../../css/core.scss, ../../css/colors.scss]
        height: 900
        width: 1600
---

# Getting a server `r fontawesome::fa(name = "server")` {background-color=var(--suso)}

## Roadmap {.suso}

::: {.box .box-1}
Access WBG demo
:::

::: {.box .box-2}
Deploy your own
:::

# Access WBG demo {background-color=var(--s1)}

## Demo {.t1}

::: {.box .box-1}
Public demo
:::

::: {.box .box-1}
Personal demo
:::

## Public demo {.t1}

:::: {.columns}

::: {.column width="70%"}
![](assets/demo_public.mp4)
:::

::: {.column width="30%"}

### Why

- Explore SuSo with mimimum setup
- Test features of latest release

### How

- Get credentials from documentation [here](https://docs.mysurvey.solutions/headquarters/config/demo-server/)
- Navigate to demo server [here](https://demo.mysurvey.solutions/) 
- Login

:::

::::

## Personal demo {.t1}

:::: {.columns}

::: {.column width="70%"}
TODO: video of process. Awaiting redacted video without sensitive info.
:::

::: {.column width="30%"}

### Why

- Test SuSo with private information
- Temporary private access

### How

- Navigate to [self-service portal](https://pds.mysurvey.solutions/)
- Log in with Designer credentails
- Request server
- Get details in email (i.e., URL, login, password)
- See more details [here](https://docs.mysurvey.solutions/headquarters/config/personal-demo-server/)

:::

::::


# Deploy you own server {background-color=var(--s2)}

## Where {.t2}

::: {.box .box-2}
Local `r fontawesome::fa(name = "building")` `r fontawesome::fa(name = "server")`
:::


::: {.box .box-2}
Cloud `r fontawesome::fa(name = "cloud")` `r fontawesome::fa(name = "server")`
:::

## Local `r fontawesome::fa(name = "building")` `r fontawesome::fa(name = "server")` {.t2}

```{r}
#| label: local
knitr::include_url("https://docs.mysurvey.solutions/headquarters/config/server-installation/", height = "600px")
```

[https://docs.mysurvey.solutions/headquarters/config/server-installation/](https://docs.mysurvey.solutions/headquarters/config/server-installation/)

## Cloud `r fontawesome::fa(name = "cloud")` `r fontawesome::fa(name = "server")` {.t2}

::: {.panel-tabset}

### AWS

```{r}
#| label: cloud-aws
knitr::include_url("https://docs.mysurvey.solutions/headquarters/config/aws-setup/", height = "600px")
```

[https://docs.mysurvey.solutions/headquarters/config/aws-setup/](https://docs.mysurvey.solutions/headquarters/config/aws-setup/)

### Azure

```{r}
#| label: cloud-azure
knitr::include_url("https://docs.mysurvey.solutions/headquarters/config/azure-setup/", height = "600px")
```

[https://docs.mysurvey.solutions/headquarters/config/azure-setup/](https://docs.mysurvey.solutions/headquarters/config/azure-setup/)

:::

## How {.t2}

::: {.box .box-2}
Manual `r fontawesome::fa(name = "screwdriver-wrench")`
:::

::: {.box .box-2}
Scripted `r fontawesome::fa(name = "file-code")`
:::

## Manual `r fontawesome::fa(name = "screwdriver-wrench")` {.t2}

```{r}
#| label: how-manual
knitr::include_url("https://docs.mysurvey.solutions/headquarters/config/aws-setup/", height = "600px")
```

[https://docs.mysurvey.solutions/headquarters/config/aws-setup/](https://docs.mysurvey.solutions/headquarters/config/aws-setup/)

## Scripted `r fontawesome::fa(name = "file-code")` {.t2}

::: {.panel-tabset}

### Azure

```{r}
#| label: how-scripted-azure
knitr::include_url("https://docs.mysurvey.solutions/headquarters/config/docker/", height = "600px")
```

[https://docs.mysurvey.solutions/headquarters/config/docker/](https://docs.mysurvey.solutions/headquarters/config/docker/)

### Docker


```{r}
#| label: how-scripted-docker
knitr::include_url("https://docs.mysurvey.solutions/headquarters/config/azure-setup/", height = "600px")
```

[https://docs.mysurvey.solutions/headquarters/config/azure-setup/](https://docs.mysurvey.solutions/headquarters/config/azure-setup/)

:::

