---
format: 
    revealjs: 
        theme: [default, ../../css/core.scss, ../../css/colors.scss]
        height: 900
        width: 1600
highlight-style: github
execute: 
  eval: false
  echo: false
---

# Procurement `r fontawesome::fa(name = "sack-dollar")` `r fontawesome::fa(name = "tablet-screen-button")` {background-color=var(--suso)}


## Roadmap `r fontawesome::fa(name = "route")` {.suso}

::: {.box .box-1}
Server `r fontawesome::fa(name = "server")`
:::

::: {.box .box-2}
Tablets `r fontawesome::fa(name = "tablet-screen-button")`
:::

::: {.box .box-3}
Routers `r fontawesome::fa(name = "wifi")`
:::

::: {.box .box-4}
Other equipment `r fontawesome::fa(name = "plug")` `r fontawesome::fa(name = "sheet-plastic")` `r fontawesome::fa(name = "battery-three-quarters")`
:::

# Server `r fontawesome::fa(name = "server") `{background-color=var(--s1)}

## Requirements {.t1}

:::: {.columns}

::: {.column width="50%"}

### Hard

```{r}
#| eval: true
knitr::include_url("https://docs.mysurvey.solutions/faq/server-requirements/", height = "600px")
```

[https://docs.mysurvey.solutions/faq/server-requirements/](https://docs.mysurvey.solutions/faq/server-requirements/)

:::

::: {.column width="50%"}

### Soft

- Supports expected load
- Scalable to increased load if needed

:::

::::

## Options {.t1}

::: {.box .box-1}
Local
:::

::: {.box .box-1}
Cloud
:::


## Local {.t1}

:::: {.columns}

::: {.column width="50%"}

### 👍

- You manage your server
- Server physically on-prem
- Data stored on-prem

:::

::: {.column width="50%"}

### 👎

- <details>
  <summary>You NEED to manage everything about your server</summary>
  <ul>
    <li>Power supply</li>
    <li>Computational resources</li>
    <li>Backup</li>
    <li>Redundancy</li>
    <li>Monitoring</li>
    <li>Security</li>
    <li>Etc.</li>
  </ul>
</details>
- You must pay for the costs of the above
- Your security is only as good as:
  - On-prem physical security
  - In-house digital security protections

:::

::::

## Cloud {.t1}

:::: {.columns}

::: {.column width="50%"}

### 👍

- Someone else manages your server infrastructure (for a small monthly fee)
- Easily scale resources as a function of needs (e.g. more RAM, more storage, etc.)
- Better security, easier
- Easy to script deployment

:::

::: {.column width="50%"}

### 👎

- Procurement requires a credit or prepaid card to pay service provider
- Deployment may require new skills (e.g., learning provider's services, how to orchestrate services, etc.)
- Clearance for cloud deployment may be harder to obtain (even if it's generally cheaper and more secure)

:::

::::


# Tablets `r fontawesome::fa(name = "tablet-screen-button")` {background-color=var(--s2)}

## Requirements {.t2}

:::: {.columns}

::: {.column width="50%"}

### Hard

```{r}
#| eval: true
knitr::include_url("https://docs.mysurvey.solutions/faq/what-tablets-should-i-buy-/", height = "600px")
```

[https://docs.mysurvey.solutions/faq/what-tablets-should-i-buy-/](https://docs.mysurvey.solutions/faq/what-tablets-should-i-buy-/)

:::

::: {.column width="50%"}

### Soft 

- More RAM -> faster performance
- Reputable manufacturer
  - Better product
  - Better (public) support
  - More updates

:::

::::

## Other considerations {.t2}

- If planning for offline interview transfer, equipped with ...
  - ... Bluetooth
  - ... WiFi Direct
- If GPS points or area matter ...
  - ... number satellite constellations (GPS, Glonas, Beidou, etc.)
  - ... Bluetooth to connect with GPS devices 

## Number to buy {.t2}

:::: {.columns}

::: {.column width="33%"}

### Field team

- Supervisor
- Interviewer

:::

::: {.column width="33%"}

### Backup

- Per team, kept with the team
- Additional, kept with the head office

:::

::: {.column width="33%"}

### Others

- For extra field staff trained but not hired
- For the head office team, to replicate issues flagged by the field

:::

::::

# Routers `r fontawesome::fa(name = "wifi")` {background-color=var(--s3)}

## Requirements {.t3}

- Connect with mobile internet service provider
- 4G or 5G connection strongly recommended

## Number to buy {.t3}

:::: {.columns}

::: {.column width="33%"}

### Field team

One per team

:::

::: {.column width="33%"}

### Backup

Kept with the head office

:::

::: {.column width="33%"}

### Others

- For extra field staff trained but not hired
- For the head office team, to be connected while on field supervision mission

:::

::::


## Other considerations {.t3}

- Mobile, with battery for autonomuous usage
- Unlocked, so can use SIM card of other internet service providers, as needed

# Other equipment `r fontawesome::fa(name = "plug")` `r fontawesome::fa(name = "sheet-plastic")` `r fontawesome::fa(name = "battery-three-quarters")` {background-color=var(--s4)}

## Charging `r fontawesome::fa(name = "plug")` `r fontawesome::fa(name = "battery-three-quarters")` {.t4}

:::: {.columns}

::: {.column width="50%"}

### Battery packs

- Smaller for each field worker (e.g., 8k mAh)
- Larger ones for teams (e.g., 30k mAh)

:::

::: {.column width="50%"}

### Charger

- Power strip, so team can charge multiple tablets at once over night
- Plug adapters, if tablet has different plug than country

:::

::::

## Protection `r fontawesome::fa(name = "sheet-plastic")` {.t4}

:::: {.columns}

::: {.column width="50%"}

### Case

- One per tablet
- Consider a small number of extras, since typically not replaced

:::

::: {.column width="50%"}

### Screen protector

- One per tablet
- Consider small number of extras, but larger number than of cases. Screen protectors might be replaced more regularly.

:::

::::


